\section[Aku Aku]{Aku Aku\ragStars{2}}\index{pineapple!Aku~Aku}\index{rum!Aku~Aku}


\begin{recipestats}[
	servings=1,
	preptime=5~\minute,
	source=\citeauthor{smugglersCove}~\cite[p.~39]{smugglersCove},
	original=\citeauthor{traderVicsGuide}~\cite{traderVicsGuide},
]
\end{recipestats}

\begin{recipeabstract}
	Originally named the Missionary's Downfall and served by Don the Beachcomber in the 1930's\cite{smugglersCove}.
	\citeauthor{smugglersCove} notes that pineapple and mint are a classic flavor combination and is again popular.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[5][$1''$]{pineapple chunk}\\
		\ingredient[8][]{mint leaves}\\
		\ingredient[1][\fluidounce]{lime juice}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onehalf][\fluidounce]{demerara syrup}\\
		\ingredient[\onehalf][\fluidounce]{peach liqueur}\\
		\ingredient[1~\onehalf][\fluidounce]{blended lightly aged rum}
	\end{ingredientblock}
\end{ingredientcolumns}

\ragmarpar{Lightly aged is $\approx [1..4]$ \Year~old, e.g.\ Mount Gay Eclipse\cite{smugglersCove}.}
\begin{preparation}
	\item Muddle pineapple chunks in a mixer tin.
	\item Add remaining ingredients.
	\item Add $12~\ounce$ crushed ice, and $[4..6]$ agitator cubes.
	\item Flash blend $10~\second$, double strain into chilled coupe.
	\item Garnish with mint leaves resting against side of glass.
\end{preparation}


\begin{variation}
	\item Apricot brandy works well too.
\end{variation}

\begin{experiments}
	\item This was a three stars at the restaraunt, but is difficult to replicate.
		How do we stop the mint from fragmenting for example?
\end{experiments}


\recipeend%
