\section[Sidewinder's Fang]{Sidewinder's Fang~\ragStars{3}}


\begin{recipestats}[
	servings=1,
	preptime=10~\minute,
	original=\citeauthor{smugglersCove}~\cite[p.~62]{smugglersCove},
]
\end{recipestats}

\begin{recipeabstract}
	An impressive drink served in a snifter with snake-shaped orange peel springing out top.
	The sweet orange flavor contrasts well with the sour passion fruit and lime.
	Brought to you by the Lanai restaraunt of San Mateo, California all the way from the 1960's~\cite{smugglersCove}.
\end{recipeabstract}
\ragmarpar{See \reffull{passionFruitSyrup}}


\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[1~\onehalf][\fluidounce]{lime juice}\\
		\ingredient[1~\onehalf][\fluidounce]{orange juice}\\
		\ingredient[1~\onehalf][\fluidounce]{passion fruit syrup}\\
		\ingredient[3][\fluidounce]{seltzer}\\
		\ingredient[1][\fluidounce]{blended aged rum}\\
		\ingredient[1][\fluidounce]{black blended rum}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
	\item Prepare the orange peel.
		Begin at the top and peel one continous strip $\approx1''$ wide by rotating the orange until you reach the equator.
		Angle the peeler at the end to create a wide diamond.
		Poke two holes to give the snake it's eyes.
	\ragmarpar{Imagine the snake hiding in the foliage of the mint.}
	\item Line the snifter w/ the peel, hanging it's head off the top.\\
		Fill w/ crushed ice.
	\item Add liquids to a tin w/ $12~\ounce$ crushed ice \& $[4..6]$ agitator cubes.
	\item Flash blend $\approx10~\second$, strain into glass, add a straw.
	\item Garnish w/ mint.
\end{preparation}


\recipeend%
