\section[Chocolate Cake]{Much Too Good for Children\\ Chocolate Cake}


\ragmarpar{natural cocoa powder (v.s. dutch process) is critical for the cake as it's more acidic}
\begin{recipestats}[
	servings=12 slices,
	preptime=1 \hour,
	bakingtime=35 \minute,
	inactivetime=$\ge1~\hour$,
	source=Mike \& Jane,
	original=\citetitle{sallyTripleChoc2020} \cite{sallyTripleChoc2020},
]
\end{recipestats}


\begin{recipeabstract}
	A decadent cake perfect for a birthday.
	Natural cocoa powder is used with buttermilk and baking soda for leavening.
	Coffee is used to enhance the chocolate flavor but it won't taste like coffee.
\end{recipeabstract}

% the ingredients env doesn't know how big it is, so for a break here
% this may change depending on the content before it, is there a better way to handle this?
\pagebreak[4]
\begin{ingredientcolumns}
	\begin{ingredientblock}[cake]
		\ingredient[220][\gram]{flour, all purpose}\\
		\ingredient[65][\gram]{cocoa powder}\\
		\ingredient[350][\gram]{sugar}\\
		\ingredient[2][\teaspoon]{baking soda}\\
		\ingredient[1][\teaspoon]{baking poweder}\\
		\ingredient[1][\teaspoon]{salt}\\
		\ingredient[3][\gram]{instant coffee}\\
		\ingredient[\onehalf][C]{vegetable oil}\\
		\ingredient[2]{eggs}\\
		\ingredient[2][\teaspoon]{vanilla extract}\\
		\ingredient[1][C]{buttermilk}\\
		\ingredient[7][\gram]{coffee beans}\\
		\ingredient[1][C]{water, hot}
	\end{ingredientblock}
	\begin{ingredientblock}[frosting]
		\ingredient[195][g]{butter, unsalted}\\
		\ingredient[280][g]{sugar, confectioners}\\
		\ingredient[45][g]{cocoa, dutch process}\\
		\ingredient[3][\Tablespoon]{cream}\\
		\ingredient[\oneeighth][\teaspoon]{salt}\\
		\ingredient[1][\teaspoon]{vanilla}\\
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\ragmarpar{take butter out of fridge now for frosting}
\item Preheat oven to 325 \Fahrenheit.
	Grease and line two 9 \inch~cake pans.

\item Grind the coffee beans and brew it.
	Add instant coffee.

\item Combine flour, cocoa powder, sugar, baking soda, salt; set aside.

\item Beat on medium high w/ a whisk: oil, eggs, vanilla; until combined.

\item Change speed to low.
	Beat in buttermilk.
	Beat in flour $\approx \onefourth~C$ at a time.
	Beat in hot coffee.

\ragmarpar{expect a thin batter}
\item Turn off mixer, scrape bowl with spatula to remove lumps.

\item Pour batter into pans and bake 35 \minute~or until done.
	Remove and let cool completely in pan.

\item Make frosting.
	Bring butter to room temperature.
	Mix sugar, cocoa, salt, set aside.
	Reserve mixer w/ paddle attachment.

\item Beat butter on medium $\approx2~\minute$.
	Add sugar mixture, cream, vanilla, then beat on low $\approx 30~\second$, then on high $\approx 60~\second$.
	Adjust viscosity w/ more sugar or cream.

\ragmarpar{refridgerate prior to serving to help maintain the shape}
\item Remove cakes from pans ad cut flat if necessary.
	Ice the cakes.

\item Refridgerate up to 5 $day$.
\end{preparation}


\begin{variation}
\item See original recipe \cite{sallyTripleChoc2020} for options with ingredients such as sour cream for a denser cake.
\end{variation}


\begin{experiments}
\item Dial in bake time.
	Reducing temperature / increasing time should reduce dome shape.
	So far trying 350 to 325 \Fahrenheit, 25 to 35 \minute.

\item Looking for a way to add marshmallow fluff between layers.

\item Dial in bake time for 6 \inch~pans.
\end{experiments}


\recipeend
