\section[Chocolate Walnut Pie]{Chocolate Cr\`{e}me de Cacao\\ Walnut Pie}

\begin{recipestats}[
	servings=1 pie,
	preptime=20 minutes,
	bakingtime=40 minutes,
	source=\citefield{pie2004}{title} \cite{pie2004},
]
\end{recipestats}

\begin{recipeabstract}
	A Teresi Thanksgiving \& Christmas tradition.
	The cr\`{e}me de cacao, molasses, and cinnamon give this pie a complex flavor.
\end{recipeabstract}

\ragmarpar{let eggs come to room temperature}
\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][C]{corn syrup}\\
		\ingredient[1][\Tablespoon]{molasses, unsulfered}\\
		\ingredient[\onefourth][C]{butter, unsalted}\\
		\ingredient[\onefourth][C]{dark chocolate chips}\\
		\ingredient[3][\Tablespoon]{cr\`{e}me de cacao}\\
		\ingredient[2][\teaspoon]{vanilla extract}\\
		\ingredient[1][\teaspoon]{espresso powder}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onehalf][C]{sugar}\\
		\ingredient[2][\Tablespoon]{flour}\\
		\ingredient[\onefourth][\teaspoon]{cinnamon}\\
		\ingredient[\oneeighth][\teaspoon]{salt}\\
		\ingredient[3][large]{eggs}\\
		\ingredient[2][C]{walnuts}
	\end{ingredientblock}
\end{ingredientcolumns}

\begin{preparation}
\item Prepare pastry \ref{basicFlakyPiePastry} \nameref{basicFlakyPiePastry}, partially pre-bake, and let cool.
\item Preheat oven to $350$ \Fahrenheit.
	Chop walnuts.
\item Heat on low until melted the corn syrup, molasses, butter.
	Add chocolate chips, remove from heat, wait $\approx 5$ $min$.
	Add cr\`{e}me de cocao and vanilla, whisk together.
\item Add to a large bowl sugar, flour, cinnamon, salt.
	Whisk in eggs, then chocolate, then walnuts.
\item Pour filling into pie shell and even out walnuts.
\item Bake $[35 \dots 40]$ $min$, rotating $180^\circ$ halfway through cooking.
	Add more time if the center is not set.
	The edges should puff up as well.
\item Remove and let cool completely.
	Serve at room temperature or refridgerated.
\end{preparation}

\begin{variation}
	\item Server with whip cream and / or vanilla icecream.
	\item \citeauthor{pie2004} \cite{pie2004} recommends a nut pastry, and trying Kahl\'{u}a in place of cr\`{e}me de cacao.
\end{variation}

\recipeend
