\section{Frankie Brownies}


\begin{recipestats}[
	servings=36,
	preptime=15 \minute~+chill,
	bakingtime=33 \minute~,
%	source=source / author,
	original=\citefield{mikesPeppermint2020}{shorttitle} \cite{mikesPeppermint2020},
]
\end{recipestats}


\begin{recipeabstract}
	A peppermint pattie brownie from scratch.
	Three layers of brownie, peppermint, and ganache.
	Currently a work in progress.
\end{recipeabstract}


\ragmarpar{use dutch process cocoa}
\begin{ingredientcolumns}
	\begin{ingredientblock}[brownie]
		\ingredient[200][\gram]{sugar}\\
		\ingredient[60][\gram]{flour}\\
		\ingredient[25][\gram]{cocoa}\\
		\ingredient[\onefourth][\teaspoon]{baking powder}\\
		\ingredient[\onefourth][\teaspoon]{salt}\\
		\ingredient[115][\gram]{butter, unsalted}\\
		\ingredient[2][large]{eggs}\\
		\ingredient[1][\teaspoon]{vanilla}
	\end{ingredientblock}
	\begin{ingredientblock}[peppermint]
		\ingredient[300][\gram]{sugar, powedered}\\
		\ingredient[15][\gram]{butter, unsalted}\\
		\ingredient[\onehalf][\teaspoon]{peppermint extract}\\
		\ingredient[\onefourth][\teaspoon]{vanilla extract}\\
		\ingredient{water}
	\end{ingredientblock}
	\begin{ingredientblock}[ganache]
		\ingredient[100][\gram]{chocolate, 60\%}\\
		\ingredient[60][\gram]{butter, unsalted}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Preheat to 350 $\Fahrenheit$.

\item Prepare $8x8~\inch$ pan: grease and insert parchment paper.
	Leave an edge large enough to lift out later.

\item Combine sugar, flour, cocoa powder, baking powder, salt.

\item Melt butter and set aside to cool.
	Whisk eggs and vanilla in another bowl.
	Slowly pour butter into eggs while whisking.

\item Mix eggs into dry ingredients until just combined.

\item Bake for $[30 \ldots 33]~\minute$, until a toothpick inserted comes clean.

\item Allow to cool completely.

\item Combine powdered sugar, butter, peppermint and vanilla extracts.
	Stir in 3 \Tablespoon~of boiling water.
	Adjust to desired consistency with additional water.

\item Pour over brownies and smooth out.
	Refridgerate $\ge 30~\minute$.

\item Melt butter and chocolate for the ganache until just smooth.
	Pour over peppermint layer.
	Refridgerate until set $\approx 1~\hour$.

\item Remove and cut into squares.
\end{preparation}


\begin{experiments}
\item Increase brownie size.
\item Move to a fudgy brownie, add butter and chocolate, remove baking powder.
\item Decrease peppermint size?
\end{experiments}


\recipeend
