\section{Italian Tricolors}

\begin{recipestats}[
	servings=36 cookies,
	preptime=1 hour (1 hour chilling),
	bakingtime=10 minutes,
	source=\citefield{goodHousekeeping_2013}{title} \cite{goodHousekeeping_2013},
	]
\end{recipestats}

\begin{recipeabstract}
	A Teresi Christmas tradition.
	The almond, apricot, and chocolate are quite complementary flavors.
	
\end{recipeabstract}

\ragmarpar{fresh almond paste is critical}
\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[8][\ounce]{almond paste}\\
		\ingredient[\threefourth][C]{butter}\\
		\ingredient[\threefourth][C]{sugar}\\
		\ingredient[\onehalf][\teaspoon]{almond extract}\\
		\ingredient[3][large]{eggs}\\
		\ingredient[1][C]{flour, all purpose}\\
		\ingredient[\onefourth][\teaspoon]{salt}\\
		\ingredient[15][drops]{red food coloring}\\
		\ingredient[15][drops]{green food coloring}\\
		\ingredient[\twothird][C]{apricot preserves}\\
		\ingredient[3][\ounce]{dark chocolate}\\
		\ingredient[2][\teaspoon]{shortening}
	\end{ingredientblock}
\end{ingredientcolumns}

\begin{preparation}
\item Preheat oven ($350\; \Fahrenheit$), grease three $8"\;x\;8"$ (square) pans.
Line bottoms w/ waxed paper, grease and flour the interior.

\ragmarpar{it's ok if a few lumps remain}
\item Blend at medium-high speed: almond paste, butter, sugar, almond extract.
Reduce to medium and add eggs one-at-a-time.
Reduce to low and beat in flour \& salt until just combined.

\item Divide batter into thirds into separate bowls.
Blend green dye into one, red into another.

\item For each mixture. transfer and spread evenly into the pans.

\item Bake on two oven racks $10-12\; minutes$ rotating pans between upper/lower halfway through.
Ensure layers are set such that a toothpick inserted in the center comes out clean.

\item Cool in pans on wire racks $5\; minutes$.
Run knife around sides to loosen layers. Invert onto racks and cool completely; removing the paper when done.

\ragmarpar{add more shortening or corn syrup to the chocolate to make it easier to cut}
\item Blend jam in food processor to remove the larger chunks.

\item Assemble layers, green / white / red, with jam between.
Heat the chocolate and shortening on low in a 1-quart saucepan, stirring frequently until melted.
Spread on top of the red layer, but not the sides, and refrigerate at least 1 hour.

\item To serve, let rest at room temperature for at least 15 minutes then trim the edges and cut into squares ($\approx36$ pieces).
Store cookies in a single layer in a tightly covered container in the refrigerator up to 1 week or in the freezer up to 3 months.
\end{preparation}

\begin{variation}
\item Other colors and jams are available. Fourth of July with red / white / blue / cherries works out nicely.
\end{variation}