\section[Lemon Meringue Pie]{Classic Lemon Meringue Pie}
\index{lemon!Lemon~Meringue}


\begin{recipestats}[
	servings=1 pie,
	preptime=1 \hour,
	bakingtime=20 \minute,
	source=\citefield{pie2004}{title} \cite{pie2004},
	]
\end{recipestats}


\begin{recipeabstract}
	A Teresi Thanksgiving \& Christmas tradition.
	This is perfect for large gatherings.
	It can be made the day prior, save for the meringue which is done before serving.
	It is light and tart which is excellent after a large meal.
\end{recipeabstract}

\pagebreak[4]
\begin{ingredientcolumns}
	\begin{ingredientblock}[filling]
		\ingredient[1 \onethird][C]{sugar}\\
		\ingredient[\threeeighth][C]{corn starch}\\
		\ingredient[\oneeighth][\teaspoon]{salt}\\
		\ingredient[2][C]{water}\\
		\ingredient[\onehalf][C]{lemon juice}\\
		\ingredient[1][\Tablespoon]{lemon zest}\\
		\ingredient[4][large]{egg yolks}\\
		\ingredient[2][\Tablespoon]{butter, unsalted}
	\end{ingredientblock}
	\begin{ingredientblock}[meringue]
		\ingredient[4][large]{egg whites}\\
		\ingredient[\onefourth][\teaspoon]{cream of tartar}\\
		\ingredient[1][pinch]{salt}\\
		\ingredient[\onehalf][C]{sugar, powdered}\\
		\ingredient[\onehalf][\teaspoon]{vanilla extract}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\ragmarpar{Fresh lemons are critical, you'll need $\geq 2$. Extra juice / zest is ok.}
\item Prepare pastry \ref{basicFlakyPiePastry} \nameref{basicFlakyPiePastry}, partially pre-bake, and let cool.
	Dice the butter into $\approx\onehalf$ $inch$ pieces.

\item Cook custard.
	Mix sugar, cornstarch, salt, in a saucepan.
	Add water, lemon juice \& zest.
	Whisk in egg yolks.
	Whisk nonstop over medium, heat, for $\approx 5\dots7$ \minute, until it boils.
	Reduce heat and continue whisking for $\approx 60 \dots 90$ \second.

\item Emulsify custard.
	Remove from heat, continue whisking, and add the butter slowly one piece at a time.

\item Cool custard.
	Pour custard into shell, let settle \& cool briefly.
	Press plastic wrap on top to keep air out and let cool to room temperature.
	Refrigerate and use within $1\; day$.

\item Prepare meringue prior to serving.
	Preheat broiler.
	Beat egg whites on medium-high to soft peaks, beat in cream of tartar \& salt.
	Slowly beat in sugar to firm or stiff peaks.
	Beat in vanilla briefly. Top the pie and broil.
\end{preparation}


\recipeend
