\section[Mango Banana Bread]{Real Deal Mango Banana Bread}
\index{banana!Mango Banana Bread}
\index{mango!Mango Banana Bread}


\begin{recipestats}[
	servings=2 loafs,
	preptime=1 \hour,
	bakingtime=1 \hour,
	original=\citeauthor{bananaMangoAlbouze}\cite{bananaMangoAlbouze},
	source=Mike \& Jane,
]
\end{recipestats}


\begin{recipeabstract}
	``The marriage between banana, lime, and mango is quite amazing\cite{bananaMangoAlbouze}.''
	The lime glaze really does take this cake up notch.
\end{recipeabstract}
\ragmarpar{About 7 bananas, 4 eggs, 6 limes, 2 mangos.}


% NOTE >2 `ingredientblock`s could be added all together w/ manual skips
% or manually create more than one `ingredientcolumns`
% or something else...
\begin{ingredientcolumns}

	\begin{ingredientblock}[banana mix]
		\ingredient[525][g]{banana}\\
		\ingredient[20][g]{lime juice}
	\end{ingredientblock}

	\bigskip
	\begin{ingredientblock}[add-ins]
		\ingredient[250][g]{chocolate chips}\\
		\ingredient[15][g]{flour}
	\end{ingredientblock}

	\bigskip
	\begin{ingredientblock}[mango mix]
		\ingredient[500][g]{mango}\\
		\ingredient[20][g]{butter}\\
		\ingredient[20][g]{brown sugar}\\
		\ingredient[10][g]{lime zest}\\
		\ingredient[15][g]{lime juice}
	\end{ingredientblock}

	\begin{ingredientblock}[batter]
		\ingredient[525][g]{pastry flour}\\
		\ingredient[270][g]{butter}\\
		\ingredient[200][g]{eggs}\\
		\ingredient[20][g]{baking powder}\\
		\ingredient[3][g]{salt}\\
		\ingredient[3][g]{baking soda}
	\end{ingredientblock}

	\smallskip
	\begin{ingredientblock}[glaze]
		\ingredient[30][g]{lime juice}\\
		\ingredient[180][g]{sugar, powdered}
	\end{ingredientblock}

\end{ingredientcolumns}

\begin{preparation}
\ragmarpar{``The final texture of the cake depends [on adding the liquid slowly to the batter]\cite{bananaMangoAlbouze}.''}
\item Save overripe bananas in freezer, thaw before using.

\item Grease and line two loaf pans, preheat oven to 350 $\Fahrenheit$.

\item Measure batter: bring butter to room temperature, beat eggs; combine flour, soda, powder; combine salt, sugar.

\item Toss chocolate chips, flour.

\item Prep mango mix: add brown sugar, butter, zest, to a frying pan for the mango;
	zest the lime and set aside.

\item Squeeze out banans, mix w/ lime juice w/ immersion blender.

\item Peel and cube mango, saut\'{e} $\approx 8$ $\minute$.
	Transfer to plate, add lime juice \& zest, let cool.

\ragmarpar{Batter can be chilled $\le5~\Day$.}
\item Cream butter, salt, sugar.
	Gradually add eggs until smooth.

\item Add $\approx~\onetenth$ flour mix on low, then banana, then remaining flour.

\item Fold chips and mango mix, fold in batter.
\ragmarpar{Top glaze w/ zest for a little pizzazz.}

\item Bake for $\approx~1$ $\hour$ or until done.
	Meanwhile, combine lime juice and powdered sugar.

\item When done baking, immediately glaze and bake for 1 $\minute$.
	Let stand 15 $\minute$ before unmolding.
	Let cool then chill overnight.
\end{preparation}
\ragmarpar{Bread can be chilled $\le5~\Day$, frozen $\le3~\Month$.}

\begin{variation}
\item The original recipe uses 200 $\gram$ chocolate chips and 220 $\gram$ walnuts.
\end{variation}


\begin{experiments}
\item Looking to replace the chips w/ Mango or strawberry; would strawberry overpower the mango?
\item Need to cut the recipe in half for a normal loaf pan.
\item Need to try fresh mango, previously had to use canned w/ syrup.
\end{experiments}


\recipeend
