\section[Felix Cookies]{Felix Cookies, or,\\ \mbox{Schwarz-Wei\ss-Geb\"{a}ck}}

\begin{recipestats}[
	servings=40 cookies,
	preptime=30 minutes (+90 min chill),
	bakingtime=12 minutes / batch,
	source=\citetitle{luisaWeiss2016} \cite{luisaWeiss2016},
	]
\end{recipestats}

\begin{recipeabstract}
	A shortbread cookie with a black and white checkerboard.
	Works very well with the addition of chocolate.
	Aliased for our black and white cats, Felix and Frankie.
\end{recipeabstract}

\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[150][g]{butter, unsalted}\\
		\ingredient[75][g]{sugar, powdered}\\
		\ingredient[\oneeighth][\teaspoon]{salt}\\
		\ingredient[\onefourth][\teaspoon]{vanilla extract}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[200][g]{flour, all purpose}\\
		\ingredient[1]{egg yolk}\\
		\ingredient[2][\Tablespoon]{whole milk}\\
		\ingredient[2\;\onehalf][\Tablespoon]{cocoa powder}
	\end{ingredientblock}
\end{ingredientcolumns}

\begin{preparation}
\ragmarpar{other shapes are available, like 6 petal flowers, spirals, etc.}
\item Cream butter $\approx 1$ $minute$, add sugar, salt, vanilla, then cream.
Add flour and mix until just combined.

\item Divide dough in half, mix cocoa into one half.
Form into disks, wrap in plastic wrap, refrigerate $\approx1$ $hour$.

\item Mix milk \& egg yolk in a small bowl.

\item Make 4 square logs, brush sides w/ egg wash, press together and refrigerate $\approx 30$ $minutes$.

\ragmarpar{don't over bake, try adding another sheet below to shield the radiation}
\item Meanwhile preheat oven \& line baking sheets with parchment paper.

\item Slice off cookies to $1cm$ or other desired thickness, bake $12...15$ $minutes$.
\end{preparation}

\begin{variation}
\item Dip into dark chocolate.
\end{variation}