\section{Seven Layer Brownies}

\begin{recipestats}[
	servings=9 brownies,
%	preptime=preparation time,
%	bakingtime=cooking time,
	source=Rand Pearson,
	]
\end{recipestats}

\begin{recipeabstract}
	A most excellent brownie recipe.
	The original was free-form so these instructions are more like guidelines.
	Try to find your inner muse and capture some of that magic.
\end{recipeabstract}

\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][box]{Betty Crocker Brownie / Cookie combo mix}\\
		\ingredient[4][\Tablespoon]{butter}\\
		\ingredient[4 \dots 6]{Heath Bars}\\
		\ingredient{marshmallows}\\
		\ingredient{graham crackers}\\
		\ingredient{chocolate chips}\\
		\ingredient{peanut butter}
	\end{ingredientblock}
\end{ingredientcolumns}

\begin{preparation}
\item Mix up the brownie and cookie mix as instructed on the box.

\item Place brownie mix in a baking dish as instructed.

\item Coarsely chop Heath bar and spread evenly over brownie batter.

\item Place cookie dough mix on top of Heath bar layer.

\item Crush graham crackers and spread over cookie dough.

\item Melt half a stick of butter and pour over graham crackers.

\item If using chocolate chips spread a layer over graham crackers.
If using peanut butter melt it and pour over graham cracker.

\item Split marshmallows lengthwise and arrange a solid layer over the top of everything.
You might also use mini marshmallows to skip cutting them.

\item Bake as instructed on brownie box. Time may increase due to the extra layers.
Brownies are done when a toothpick comes out clean.
\end{preparation}


\begin{experiments}
\item Keep in mind that there really isn't a recipe since I just made it all up as I went along. What you should take from that is this: Feel free to experiment; any problems can be overcome with enough butter and sugar. I'm pretty sure this is also true in life.

\item In the future I was considering leaving the marshmallows off until I take the brownies out of the oven, then adding them ad hitting them with a torch.
\end{experiments}

\recipeend
