\section[Strawberry Rhubarb Pie]{Strawberry Rhubarb Crumb Pie}


\begin{recipestats}[
	servings=1 pie,
	preptime=1 \onehalf~\hour,
	bakingtime=50 \minute,
	source=\citefield{pie2004}{title} \cite{pie2004},
	]
\end{recipestats}


\begin{recipeabstract}
	I don't always have favorites but when I do it's pretty close to this pie.
	Make sure to capitalize on the spring season when rhubarb is available.
	There is a lot of liquid so I increased the tapioca and maceration time.
	Make sure to use a deep pan and high crust.
\end{recipeabstract}


\ragmarpar{don't eat the rhubarb leaves}

\begin{ingredientcolumns}
	\begin{ingredientblock}[filling]
		\ingredient[3][C]{rhubarb}\\
		\ingredient[\threefourth][C]{sugar}\\
		\ingredient[1 \onehalf][\Tablespoon]{lemon juice}\\
		\ingredient[1][lemon]{zest}\\
		\ingredient[4][C]{strawberries}\\
		\ingredient[\onehalf][C]{tapioca, quick}
	\end{ingredientblock}
	\begin{ingredientblock}[topping]
		\ingredient[\threefourth][C]{flour, all-purpose}\\
		\ingredient[\onefourth][C]{cornmeal, yellow}\\
		\ingredient[\twothird][C]{sugar, brown}\\
		\ingredient[\onehalf][\teaspoon]{cinnamon}\\
		\ingredient[\onefourth][\teaspoon]{salt}\\
		\ingredient[\onehalf][C]{butter, unsalted}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Prepare \ref{basicFlakyPiePastry} \nameref{basicFlakyPiePastry} and refrigerate $\geq 1$ \hour.

\ragmarpar{make a high crust to prevent spills}
\item Roll pastry onto wax paper $\approx 13"$ diameter, invert onto pie pan and shape.
	Freeze for 15 \minute.
	Preheat oven to $400$ \Fahrenheit.

\item Prepare filling.
	Slice rhubarb $\approx 1/2"$ pieces, mix fruit w/ sugar, lemon juice, zest, tapioca.
	Quarter strawberries and mix in.
	Macerate for $\geq 15$ \minute.

\item Add filling evenly into crust, bake on center rack 30 \minute.

\item Meanwhile prepare topping.
	Combine flour, cornmeal, brown sugar, cinnamon, salt.
	Cut butter into pieces and blend in with food processor or pastry cutter.
	Make large crumbs by rubbing the mixture between your hands.
	Refridgerate.

\ragmarpar{place a cookie sheet underneath to catch spills}
\item Remove pie and reduce oven to 375 \Fahrenheit.
	Add crumbs to top of pie.
	Rotate pie $180^\circ$ (to bake evenly) and bake $[30...40]$ \minute.
	Add foil heat shield if needed for last $\approx 10$ \minute.
	Cool $\geq 1$ \hour.
\end{preparation}


\begin{variation}
\item Try a bit of ground green cardamom in the filling.
\end{variation}


\recipeend
