\section{Chorip\'{a}n}


\begin{recipestats}[
	servings=1,
	preptime=5~\minute,
	bakingtime=15~\minute,
	source=Mike,
	original=\citefield{wikiChoripan}{title}~\cite{wikiChoripan},
]
\end{recipestats}


\begin{recipeabstract}
	Chorip\'{a}n, or sausage-bread, is a grilled sandwich of chorizo and chimichurri.
	The spicy chorizo pairs well with the tangy sauce.
	Variants are popular in Argentina, Brazil, Chile, United States, and Uruguay.
	Other condiments can include for example cheese, pickles, mayo, mustard.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][link]{chorizo}\\
		\ingredient[1][]{baguette}\\
		\ingredient[\onefourth][C]{parsley}\\
		\ingredient[\onefourth][C]{olive oil}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[1][\fluidounce]{vinegar, red}\\
		\ingredient[3][clove]{garlic}\\
		\ingredient[1][\teaspoon]{oregano}\\
		\ingredient[1][\teaspoon]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Remove casing after flattening to prevent curling.}
\begin{preparation}
\item Heat an iron skillet on medium low.
\item Chop parsley, crush garlic,
	combine with oil, vinegar, oregano.
\item Slice the baguette to the length of the sausage.
\item Butterfly the chorizo in lengthwise, flatten.
\item Add oil to pan, grill chorizo on medium until browned.
\ragmarpar{Try a little ghee with the bread.}
\item Add bread to pan and toast a few minutes.
\item Remove bread, add chimichurri, sausage, more chimichurri.
\end{preparation}


\begin{experiments}
\item Try the other styles, maybe add red onion / tomato, mayo.
\end{experiments}


\recipeend%
