\section[Curry Rice]{Curry Rice, or, Kar\=e Raisu}


\begin{recipestats}[
	servings=4,
	preptime=10 \minute,
	bakingtime=30 \minute,
	source=Mike,
	original=\citeauthor{sbfoodsCurry} \cite{sbfoodsCurry},
]
\end{recipestats}


\ragmarpar{Also see \cite{gaijinCookbook}}
\begin{recipeabstract}
	Curry Rice is a Japanese style 'curry'.
	A stew of vegetables and meat with a side of rice.
	Instant curry roux makes it very easy to prepare and the ingredients keep well.
\end{recipeabstract}


% TODO need to weigh vegetables
\ragmarpar{S\&B 'Golden Curry' hot is best (although my options are limited)}
\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[1][\pound]{chicken thighs, skinless}\\
		\ingredient[1][small]{onion}\\
		\ingredient[2][medium]{potatoes, waxy}\\
		\ingredient[2][large]{carrots}\\
		\ingredient[92][\gram]{Japanese curry mix}\\
		\ingredient[1][\teaspoon]{chile d\`{e} arbol}\\
		\ingredient[1][C]{rice, uncooked}\\
		\ingredient[1][\Tablespoon]{black bean garlic sauce}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Short grain rice is best}


\begin{preparation}
\item Add dash of oil to a saut\'{e} pan and heat to medium high.

\item Dice chicken $\approx1x1~\inch$ and toss into pan.

\item Fry for $\approx 5~\minute$, deglaze with water.

\item Reduce to medium.
	Stir and deglaze w/ water as necessary.

\item Meanwhile dice onion and toss into chicken.

\ragmarpar{Uneven slicing while rotating is called 'rangiri'}
\item Meanwhile, dice potatoes $\approx \frac{1}{2} x \frac{1}{2}~\inch$.
	Cut carrot once lengthwise then cut diagonally while rotating.

\item Microwave carrots and potatoes together for 4 \minute.
\ragmarpar{Microwaving reduces cook time a lot}

\item Meanwhile cook your rice according to your instructions.

\item When you chicken is copper in color (or to your preference), add vegetables.
	Add $2 \onefourth~C$ water, bring to boil.
	Reduce to simmer and cook $10~\minute$.

\item Add curry roux and stir well until completely dissolved.
	Optionally add black bean garlic sauce.
	Simmer $\approx5~\minute$ more.

\item Serve with rice.
\end{preparation}


\begin{variation}
\item Combining roux varieties is common.

\item Sweet curry with apple and honey is common.

\item Adding flavorings to make your curry unique is common, e.g. tonkatsu, worcestershire, chocolate, coffee, ketchup, cream, etc.
\end{variation}


\recipeend
