\section[Chocolate Oreo]{Chocolate Marshmallow Oreo Ice Cream Extravaganza}
\index{chocolate!Chocolate~Marshmallow~Oreo~Ice~Cream}
\index{Oreo!Chocolate~Marshmallow~Oreo~Ice~Cream}
\index{Marshmallow!Chocolate~Marshmallow~Oreo~Ice~Cream}


\begin{recipestats}[
	servings=5 $C$,
	preptime=10 \minute,
	bakingtime=30 \minute,
	inactivetime=24 \hour,
	source=Mike \& Jane,
	original=\citefield{joyofcooking2006}{title} \cite{joyofcooking2006},
	]
\end{recipestats}


\begin{recipeabstract}
	A special treat best made ahead of time.
	We use a KitchenAid ice cream bowl and definitely recommend.
	Adapt recipe to your tools or method.
	If you freeze the bowl prior, you can make the cream on the first night, the ice cream the next morning, and serve the next night.
\end{recipeabstract}


\ragmarpar{Dutch process cocoa is best.}
\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[2][C]{milk, whole}\\
		\ingredient[1][C]{heavy cream}\\
		\ingredient[\onehalf][C]{sugar}\\
		\ingredient[\onefourth][C]{sugar}\\
		\ingredient[4]{egg yolks}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onethird][C]{cocoa powder}\\
		\ingredient[1][\teaspoon]{vanilla}\\
		\ingredient[1][\teaspoon]{coffee, dried}\\
		\ingredient[\approx1][C]{Oreos, chopped}\\
		\ingredient[\approx1][C]{marshmallow fluff}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{$8$ Oreos for $1\;C$}


\begin{preparation}
\item Move the ice cream bowl to the freezer, chill $\ge15$ $\hour$ before use.

\item Reserve one sauce pan, two large bowls, one airtight container.

\item Set aside the sugar, cocoa.
	Separate egg yolks into a bowl.

\item Combine in saucepan over medium low heat the milk, \onehalf~cups sugar, coffee.
	Bring to light simmer stirring occasionally.

\item Whisk egg yolks, \onefourth~$C$ sugar in a medium bowl, whisk in cocoa.

\ragmarpar{Mix slowly to prevent curdling.}
\item Pour slowly while stirring constantly about half of the hot milk into the eggs.
	Pour back into the saucepan.

\item Cook stirring constantly over low heat until it reaches 175 \Fahrenheit, and do not allow it to boil.
	Remove from heat.

\item Strain through a fine sieve into a bowl, then add cream \& vanilla.
	Freeze $\ge8$ $\hour$.

\item Assemble ice cream bowl.
	Chop oreos and set aside in freezer.

\item Add batter to bowl, stir on low $13$ $\minute$.
	Add oreos, stir $2$ $\minute$.

\ragmarpar{Don't bother measuring the fluff, just eyeball it.}
\item Spoon ice cream into an airtight container, occasionally folding in small scoops of marshmallow.
	Freeze $\ge8$ $\hour$.
\end{preparation}


\recipeend
