\section[Spekulatius]{Almond Spekulatius}\index{almond!Spekulatius}\index{cookie!Spekulatius}\index{Christmas!Spekulatius}


\ragmarpar{shpee-coo-LAH-tsi-us}
\begin{recipestats}[
	servings=servings,
	preptime=45 \minute~(+chill),
	bakingtime=10 \minute,
]
\end{recipestats}


\begin{recipeabstract}
	A spiced Christmas biscuit molded into a holiday shape.
	The molds are typically wooden with mirror reliefs that the dough is pressed into.
	German recipes often use baker's ammonia in place of baking powder which produces a crispier texture.
\end{recipeabstract}
\ragmarpar{baker's ammonia is malodorous but will dissipate when baked}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[250][\gram]{flour}\\
		\ingredient[50][\gram]{almond meal}\\
		\ingredient[100][\gram]{sugar}\\
		\ingredient[1][C]{butter, unsalted}\\
		\ingredient[1]{egg}\\
		\ingredient[1][\teaspoon]{cocoa}\\
		\ingredient[\onefourth][\teaspoon]{baker's ammonia}\\
		\ingredient[1][\Tablespoon]{milk}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onehalf][\teaspoon]{vanilla extract}\\
		\ingredient[\onehalf][\teaspoon]{almond extract}\\
		\ingredient[\threefourth][\teaspoon]{cinnamon}\\
		\ingredient[\onefourth][\teaspoon]{anise}\\
		\ingredient[\onefourth][\teaspoon]{coriander}\\
		\ingredient[\onefourth][\teaspoon]{cardamom}\\
		\ingredient[\onefourth][\teaspoon]{clove}\\
		\ingredient[1][\gram]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Measure and grind dry spices.

\item Measure and sift together flour, almond meal, cocoa, baker's ammonia, dry spices, salt.

\item Cream butter, sugar with mixer.
	Beat in egg, vanilla/almond extracts, milk.
	Blend in the flour mixture on low until combined.

\item Form the dough into a ball and cover in plastic wrap.
	Chill overnight or $\ge 2$ \hour.

\item Preheat oven to 350 \Fahrenheit.
	Oil and flour your mold.
	Grease two cookie sheets.

\item If using a spekulatius mold, press a dough ball into it and release with a knife and / or by tapping onto a table.

\item If using a springerle mold or rolling pin, roll out onto a floured surface $\approx \onehalf~cm$ thick, press mold onto sheet and cut out the cookies.

\item Bake each sheet $\approx 10$ \minute~and cool.
\end{preparation}

\ragmarpar{Dutch and French versions are called \textit{Speculaas} or \textit{Speculoos}.}
\begin{variation}
\item Brown sugar can be used instead of white.
\end{variation}

\begin{experiments}
\item Baker's ammonia can be replaced with baking powder.
	It appears more baking powder by volume is used than baker's ammonia.
\end{experiments}


\recipeend%
