\section[Applesauce Brownies]{Applesauce Brownies}\index{chocolate!Applesauce~Brownies}\index{brownies!Applesauce~Brownies}


\ragmarpar{Scott likes this.}
\begin{recipestats}[
	servings=16,
	preptime=15~\minute,
	bakingtime=35~\minute,
	source=Pam \& Sonia,
]
\end{recipestats}


\ragmarpar{I omit the nuts.}
\begin{recipeabstract}
	A chocolate brownie made light and fluffy by applesauce.
	``By the time Scott was a senior at Tabb I had started to call these Cross Country Brownies because the boys asked me so often to make them.
	Any far away meet (Cross Country or Track) they were sure to ask for them.
	Sonia gave me the recipe when we went to N.C. with [Lou and Sona in 1993].'' -Pamela
\end{recipeabstract}


\ragmarpar{Do not use dutch process cocoa due to the acidity.}
\begin{ingredientcolumns}
	\begin{ingredientblock}[brownie]
		\ingredient[2][C]{applesauce}\\
		\ingredient[2][C]{flour}\\
		\ingredient[1 \onehalf][C]{sugar}\\
		\ingredient[\onehalf][C]{oil}\\
		\ingredient[2][large]{eggs}\\
		\ingredient[2][\Tablespoon]{cocoa}\\
		\ingredient[1 \onehalf][\teaspoon]{soda}\\
		\ingredient[\onehalf][\teaspoon]{cinnamon}\\
		\ingredient[\onehalf][\teaspoon]{salt}
	\end{ingredientblock}
	\begin{ingredientblock}[topping]
		\ingredient[6][\ounce]{chocolate chips}\\
		\ingredient[\onehalf][C]{chopped nuts}\\
		\ingredient[2][\Tablespoon]{sugar}
	\end{ingredientblock}
\end{ingredientcolumns}


\pagebreak[1] % enforce break w/ pagebreak
\begin{preparation}
\item Grease a $9\times13$ $\inch$~pan, preheat to $350$ \Fahrenheit.
\item Combine brownie ingredients, beat just until smooth.
\item Pour batter into pan
\item Sprinkle topping over batter.
\item Bake for 35 \minute.
\end{preparation}


\recipeend%
