\section{Frankie Brownies}\index{chocolate!Frankie Brownies}\index{mint!Frankie Brownies}\index{brownies!Frankie Brownies}


\begin{recipestats}[
	servings=36,
	preptime=15 \minute,
	bakingtime=30 \minute,
	inactivetime=2 \hour,
	source=Mike \& Jane,
	original=\citefield{mikesPeppermint2020}{shorttitle}~\cite{mikesPeppermint2020},
]
\end{recipestats}


\begin{recipeabstract}
	A peppermint pattie brownie from scratch.
	Three layers of brownie, peppermint, and ganache.
	Currently a work in progress.
\end{recipeabstract}


\ragmarpar{Dutch process cocoa is best.}
\begin{ingredientcolumns}
	\begin{ingredientblock}[brownie]
		\ingredient[50][\gram]{sugar}\\
		\ingredient[200][\gram]{brown sugar}\\
		\ingredient[60][\gram]{flour}\\
		\ingredient[25][\gram]{cocoa}\\
		\ingredient[169][\gram]{butter, unsalted}\\
		\ingredient[50][\gram]{chocolate, 60\%}\\
		\ingredient[2][large]{eggs}\\
		\ingredient[\onehalf][\teaspoon]{salt}\\
		\ingredient[\onefourth][\teaspoon]{baking powder}\\
		\ingredient[1][\teaspoon]{vanilla}\\
		\ingredient[1][\teaspoon]{instant coffee}
	\end{ingredientblock}

	\bigskip
	\begin{ingredientblock}[peppermint]
		\ingredient[280][\gram]{sugar, powdered}\\
		\ingredient[15][\gram]{butter, unsalted}\\
		\ingredient[\onehalf][\teaspoon]{peppermint extract}\\
		\ingredient[\onefourth][\teaspoon]{vanilla extract}
	\end{ingredientblock}

	\bigskip
	\begin{ingredientblock}[ganache]
		\ingredient[100][\gram]{chocolate, 60\%}\\
		\ingredient[60][\gram]{butter, unsalted}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Prepare $8 \times 8~\inch$ pan: grease and insert parchment paper.
	Leave an edge large enough to lift out later.
	Preheat to 350 $\Fahrenheit$.

\item Melt butter and chocolate, set aside.

\item Beat eggs, sugar, vanilla.

\item Combine flour, cocoa powder, baking powder, salt, coffee.

\item Mix chocolate into eggs slowly.
	Fold wet ingredients into dry.

\ragmarpar{Halfway through baking remove and slam on the counter, this helps it set evenly.}
\item Bake for $[25 \ldots 30]~\minute$.
	The center will still be slightly wet.
	Allow to cool completely.

\item Combine powdered sugar, butter, peppermint and vanilla extracts.
	Stir in boiling water \onehalf~\teaspoon~at a time.
	Mixture should be thick.

\item Pour over brownies and smooth out.
	Refrigerate $\ge 30~\minute$.

\item Melt butter and chocolate for the ganache until just smooth.
	Pour over peppermint layer.
	Refrigerate until set $\approx 1~\hour$.

\item Remove and cut into squares.
\end{preparation}


\begin{experiments}
\item Need to stop center from falling, add more flour?
\item Need to find best amount of water to reduce peppermit viscosity.
\end{experiments}


\recipeend%
