\section[Frankie Deluxe]{Frankie Deluxe Cookies}\index{chocolate!Frankie Deluxe}\index{mint!Frankie Delux}


\begin{recipestats}[
	servings=16,
	preptime=1 \hour,
	bakingtime=12 \minute,
	source=Mike \& Jane,
	original=\citefield{sallyBrownies2020}{title}~\cite{sallyBrownies2020},
]
\end{recipestats}


\begin{recipeabstract}
	Brownies in cookie form with a peppermint pattie center.
	The recipe is a little involved but is worth it for those that appreciate brownies and peppermint.
\end{recipeabstract}


\ragmarpar{Dutch process cocoa is best, and Ghiradelli chocolate is best.}
\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[8][\ounce]{chocolate, $60\%$}\\
		\ingredient[95][\gram]{flour}\\
		\ingredient[18][\gram]{cocoa powder}\\
		\ingredient[5][\Tablespoon]{butter, unsalted}\\
		\ingredient[1][\Tablespoon]{milk powder}\\
		\ingredient[1][\teaspoon]{coffee powder}\\
		\ingredient[1][\teaspoon]{baking powder}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onefourth][\teaspoon]{salt}\\
		\ingredient[\threefourth][C]{brown sugar}\\
		\ingredient[\onefourth][C]{sugar}\\
		\ingredient[2]{eggs}\\
		\ingredient[1][\teaspoon]{vanilla}\\
		\ingredient[16][thin]{peppermint patties}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Each peppermint pattie is $\approx 8~grams$.}


\begin{preparation}
\item Bring eggs \& butter to room temperature.

\item Melt the chocolate.
	Add it to a small bowl, microwave $\approx 15$ \second, stir, repeat until melted.
	Set aside to cool slightly.

\item Mix dry ingredients except the sugar in a large bowl.

\item Cream on medium high the butter, brown sugar, white sugar.
	Add eggs, vanilla, mix well.
	Add chocolate slowly while mixing.

\item Gradually beat in the dry ingredients on low until combined.

\item Chill dough in the mixing bowl for 10 \minute.
	Preheat oven to 350 \Fahrenheit.
	Unwrap peppermint patties.
	Grease two cookie sheets.

\item Assemble cookies in batches.
	Scoop out $\approx2$ \Tablespoon, flatten out and sandwich around a peppermint pattie.
	Pinch the dough on the perimeter to close and roll to shape.
	Arrange on a cookie sheet.

\item Move the cookie sheet to the fridge for $\approx 10$ \minute.
	Bake $\approx 10$ \minute, or until edges are set.
	The center should be mostly soft and will set as it cools.
	Transfer to a wire rack when it solidifies.
\ragmarpar{Store with a piece of bread or an apple slice to prevent from drying out.}
\end{preparation}

\begin{variation}
\item The original uses chocolate chips instead of peppermint patties.
\end{variation}


\begin{experiments}
\item The chill time significantly affects the spread.
	\citeauthor{sallyBrownies2020}~\cite{sallyBrownies2020} recommends 20 \minute, but recommends 15 \minute~out on the counter if it cools too much.
	Here we need the dough to be less firm to shape.
	These instructions may need further modifications so that each batch is consistent after the first chill of the dough.
\end{experiments}


\recipeend%
