\section{Italian Tricolors}\index{almond!Italian~Tricolors}\index{Christmas!Italian~Tricolors}


\begin{recipestats}[
	servings=36 cookies,
	preptime=1 \hour,
	bakingtime=12 \minute,
	inactivetime=15 \minute,
	source=Teresi Family,
	original=\citefield{goodHousekeeping_2013}{title}~\cite{goodHousekeeping_2013},
	]
\end{recipestats}


\begin{recipeabstract}
	A Teresi Christmas tradition.
	The almond, apricot, and chocolate are quite complementary flavors.
\end{recipeabstract}


\ragmarpar{Fresh almond paste is critical.}
\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[8][\ounce]{almond paste}\\
		\ingredient[\threefourth][C]{butter}\\
		\ingredient[\threefourth][C]{sugar}\\
		\ingredient[\onehalf][\teaspoon]{almond extract}\\
		\ingredient[3][large]{eggs}\\
		\ingredient[1][C]{flour}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onefourth][\teaspoon]{salt}\\
		\ingredient[15][drops]{red coloring}\\
		\ingredient[15][drops]{green coloring}\\
		\ingredient[\twothird][C]{apricot preserves}\\
		\ingredient[3][\ounce]{dark chocolate}\\
		\ingredient[2][\Tablespoon]{shortening}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Preheat oven to $350$ \Fahrenheit.

\item Grease three $8\times8''$ pans, line with parchment paper.

\ragmarpar{It's ok if a few lumps remain.}
\item Blend at medium-high speed: almond paste, butter, sugar, almond extract.
Reduce to medium and add eggs one at a time.
Reduce to low and beat in flour \& salt until just combined.

\item Divide batter into thirds; blend green dye in one, red in another.

\item Transfer and spread each into the pans.

\item Bake on two oven racks $10 \dots 12$ \minute~rotating between upper / lower halfway through.

\item Cool in pans on wire racks 5 \minute,
	then use the paper to pull out cakes and let cool.

\item Blend jam in food processor w/ $1~\Tablespoon$~apricot brandy.

\item Assemble layers, green / white / red, with jam between.
	Melt on low chocolate / shortening, stirring frequently.
	Spread on top then refrigerate $\geq1$ \hour.

\ragmarpar{Score chocolate w/ knife before slicing to prevent fractures.}
\item Rest at room temperature for $\geq 15$ \minute~then trim the edges.

\item Cut into $\approx 1\times 1''$~or $\approx 1\times \onehalf''$~rectangles.

\item Store cookies in a single layer in a tightly covered container.
	Refrigerate $\approx 1$ \week~or freeze $\approx 3$ months.
\end{preparation}


\begin{variation}
\item Other colors and jams are available.
	Fourth of July with red / white / blue / cherries works out nicely.
\end{variation}


\begin{experiments}
\item Replace shortening in chocolate with corn syrup / butter to improve flavor and reduce viscosity?
	% https://www.epicurious.com/recipes/food/views/bittersweet-chocolate-glaze
\end{experiments}


\recipeend%
