\section{Frankie Cookies}\index{chocolate!Frankie~Cookies}\index{mint!Frankie~Cookies}\index{cookies!Frankie~Cookies}


\begin{recipestats}[
	servings=16 cookies,
	preptime=30 \minute,
	bakingtime=12 \minute,
	source=Mike \& Jane,
	original=\citetitle{entenmanns2011}~\cite{entenmanns2011},
]
\end{recipestats}


\ragmarpar{Each peppermint pattie is $\approx 8~grams$.}
\begin{recipeabstract}
	A chocolate cookie with a peppermint pattie center.
	Simple and quick.
	Aliased for our black and white cats, Felix and Frankie.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[\onehalf][C]{butter, salted}\\
		\ingredient[1][C]{sugar}\\
		\ingredient[1][large]{egg}\\
		\ingredient[\onehalf][\teaspoon]{vanilla}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[1][C]{flour}\\
		\ingredient[\onethird][C]{cocoa powder}\\
		\ingredient[\onehalf][\teaspoon]{baking soda}\\
		\ingredient[16][thin]{peppermint patties}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Don't use Dutch process cocoa, it won't leven properly.}


\begin{preparation}
\item Remove butter \& eggs from refrigerator.
	Soften the butter.
	Reserve and grease two cookie sheets.

\item Preheat oven to 350 \Fahrenheit.

\item Add butter, sugar to a mixing bowl.

\item Mix flour, cocoa, baking soda to another bowl.

\item Cream butter \& sugar on medium high $\approx 2$ \minute.

\item Mix in egg \& vanilla.

\item Mix in dry ingredients.

\ragmarpar{Make sure the edges are covered to prevent leaks.}
\item Wrap the peppermint pattie in $\approx1~\Tablespoon$.
	Top with sprinkles.

\item Refrigerate $\approx 15$ \minute, then bake 12 \minute.
\end{preparation}


\recipeend%
