\section[Berry Crisp]{Berry Crisp Ice cream}\index{cherry!Berry~Crisp~Ice~cream}


\begin{recipestats}[
    servings=16,
    preptime=15~\minute,
    bakingtime=45~\minute,
    inactivetime=4~\hour,
    original=\citetitle{jenisIcecream}~\cite[p.~148]{jenisIcecream},
]
\end{recipestats}


\begin{recipeabstract}
    Vanilla ice cream with a cherry swirl and crunchy streusel.
\end{recipeabstract}


\begin{ingredientcolumns}
    \begin{ingredientblock}
        \ingredient[2~\twothird][C]{whole milk}\\
        \ingredient[5][\teaspoon]{corn starch}\\
        \ingredient[2][\ounce]{cream cheese}\\
        \ingredient[\oneeighth][\teaspoon]{salt}
    \end{ingredientblock}
    \begin{ingredientblock}
        \ingredient[1~\onehalf][C]{heavy cream}\\
        \ingredient[\threefourth][C]{sugar}\\
        \ingredient[\onefourth][C]{corn syrup}\\
        \ingredient[1][bean]{vanilla}
    \end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Freeze your ice cream bowl 1 or 2 $\Day$ ahead.
\item Reserve a sauce pot, 3 bowls, and a 1 $\gallon$~plastic bag.
\item Mix the cornstarch with $\approx 2$ $\Tablespoon$ of milk in a small bowl.
\item Whisk the cream cheese and salt in a medium bowl.
\item Fill a large bowl with ice and water.
\item Slice the bean pod open and scrape out the seeds.
\item Add to a sauce pot:\\cream, sugar, corn syrup, vanilla seeds, pod, remaining milk.
\item Bring to a rolling boil over medium-high, boil 4 $\minute$.
\item Remove from heat, gadually mix in cornstarch.
\item Bring back to boil over medium high,\\cook while stirring $\approx~1$ $\minute$, until thickened.
\item Remove from heat.
\item Gradually whisk hot milk into cream cheese until smooth.
\item Pour into a 1 $\gallon$~plastic bag, submerge in ice bath.
\item Wait until it's cool, $\approx 30$ $\minute$.
\ragmarpar{It's done when the ice cream pulls away from the sides of the freezer bowl.}
\item Remove the bean pod, transfer milk to freezer bowl.
\item Spin until thick, $\approx 25$ $\minute$.
\item Pack into a container.
\item Press a sheet of parchment paper on top of ice cream.
\item Freeze in freezer $\ge4$ $\hour$.
\end{preparation}


\recipeend%
