\section[Pomegranate Sorbet]{Jane's Pom-Cran Sorbet}\index{pomegranate!Pom-Cran~Sorbet}


\begin{recipestats}[
	servings=12,
	preptime=15~\minute,
	bakingtime=45~\minute,
	inactivetime=8~\hour,
	original=\citefield{cranberrySorbetVegetarianBaker}{shorttitle}~\cite{cranberrySorbetVegetarianBaker},
]
\end{recipestats}


\begin{recipeabstract}
	A tart sorbet.
	We like this for Thanksgiving as it's a light after dinner desert, similar to the Thanksgiving lemon meringue.
	It's useful for family events as it's vegan.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}[pomegranate juice]
		\ingredient[3][C]{cranberries}\\
		\ingredient[1][C]{Pomegranate}\\
		\ingredient[2][C]{water}\\
		\ingredient[\onehalf][C]{sugar}
	\end{ingredientblock}

	\columnbreak
	\bigskip
	\begin{ingredientblock}[citrus juice]
		\ingredient[\onethird][C]{orange juice}\\
		\ingredient[\onehalf][C]{lemon juice}\\
		\ingredient[\onefourth][C]{lime juice}
	\end{ingredientblock}

	\bigskip
	\begin{ingredientblock}[syrup]
		\ingredient[2][C]{sugar}\\
		\ingredient[3][C]{water}
	\end{ingredientblock}

\end{ingredientcolumns}


\ragmarpar{That's $\onehalf$~pomeg-ranate, 12~$\ounce$ cranberries.}
\begin{preparation}
\item Freeze your ice cream bowl $\left[24 .. 48\right)$ $\hour$ ahead.
\item Reserve two small pots and a blender.
\item Make simple syrup in the first pot.\\
	Add $2$ $C$ sugar, 3 $C$ water.\\
	Heat on medium, dissolve completely, take off heat.
\item Meanwhile, make the pomegranate juice in the second pot.\\
	Wash the cranberries and seed the pomegranate, add.\\
	Add 2 $C$ water, $\onehalf$ $C$ sugar.
\item Simmer on medium $\approx [10..15]$ $\minute$ or until cranberries burst.
\item Move to a blender, blend on high until smooth, strain well.
\ragmarpar{Try freezing in two batches.}
\item Let syrup \& pomegranates cool; refrigerate $\ge3$ $\hour$.
\item Juice the lemons, limes, oranges.\\
	Mix juice, syrup, and pomegranate mix in large bowl, whisk.
\item Freeze in ice cream bowl according to those directions.
\item Solidify in freezer $>2$ \hour.
\end{preparation}


\recipeend%
