\section[Collard Greens]{Thanksgiving Collard Greens}
\index{collards!Collard~Greens}


\begin{recipestats}[
	servings=[4 \ldots 6] people,
	preptime=30 \minute,
	bakingtime=[2 \ldots 6] \hour,
	]
\end{recipestats}

\begin{recipeabstract}
	These are similar to southern-style collards in that they are simmered for a long time with meat.
	Turkey was substituted here for ham as an experiment for thanksgiving, partly due to availability.
	The stock can also be used to make gravy and can be very flavorful.
\end{recipeabstract}


\ragmarpar{smoked turkey necks works best}
\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][lb]{collards}\\
		\ingredient[2][]{turkey necks}\\
		\ingredient[6][C]{water}\\
		\ingredient[2][Tbs]{butter}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[2][Tbs]{vinegar}\\
		\ingredient[1][tsp]{sugar}\\
		\ingredient[1][tsp]{pepper}\\
		\ingredient[1][tsp]{hot sauce}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Make stock with turkey necks: cover with cold water, cook over high heat, bring to simmer, skim off foam from surface, reduce to $\approx 180$ \Fahrenheit. Simmer for $1 \ldots 4$ \hour.

\item Prepare collards greens ($\approx 15$ \minute~prior to removing turkey necks).
	Clean \& rinse collard greens, cut off the main stem, dice $\|$ tear greens (into $\approx 1x1"$ rectangles).

\item Remove turkey necks and sieve out undesired particulates.

\item Add greens, simmer $\approx 1$ \hour uncovered.

\item Meanwhile, remove and dice meat from turkey necks according to your preference. Add to pot.

\item Add butter, vinegar, spices, serve.
\end{preparation}

\begin{experiments}
	\item This was more of a quick experiment, it would be good to find a more traditional recipe.
	\item The stock was good but removing the meat was quite labor intensive for Thanksgiving day. This recipe might benefit from making the stock ahead of time and giving it a bit more spices \& vegetables.
\end{experiments}


\recipeend
