\section{Lasanga Soup}
\index{pasta!Lasagna~Soup}
\index{sausage!Lasagna~Soup}


\begin{recipestats}[
	servings=4,
	preptime=25 \minute,
	bakingtime=25 \minute,
	source=Mike \& Jane,
	original=\citetitle{foodNetworkLasagnaSoup} \cite{foodNetworkLasagnaSoup},
]
\end{recipestats}


\begin{recipeabstract}
	A fairly simple soup of lasagna.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[8][\ounce]{lasgna noodles}\\
		\ingredient[\onehalf][\pound]{Italian sausage}\\
		\ingredient[1]{onion, white}\\
		\ingredient[4][cloves]{garlic}\\
		\ingredient[1][\teaspoon]{oregano}\\
		\ingredient[1][\teaspoon]{marjoram}\\
		\ingredient[2][\Tablespoon]{tomato paste}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[1][bottle]{Chianti}\\
		\ingredient[4][C]{broth}\\
		\ingredient[15][\ounce]{tomatoes, crushed}\\
		\ingredient[\onehalf][C]{basil}\\
		\ingredient[\onehalf][C]{parmesan}\\
		\ingredient[\onefourth][C]{cream}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Reserve a $\geq 3.5~\quart$ pot for both the soup \& noodles.

\item Break the noodles into pieces.
	Chop the onion.
	Smash then peel the garlic.

\item Cook the noodles al dente and toss with oil.

\ragmarpar{hot Italian sausage is best}
\item Meanwhile brown the sausage on medium high.
	Stir and break apart the sausage until browned, deglaze w/ some Chianti.

\item Add the oregano, marjoram, onion, cook $[2 \ldots 4]$ \minute.

\item Add the tomato paste and garlic, saute\`{e} $[1 \ldots 2]$ \minute.

\item Add the broth and tomatoes, simmer $\approx 10$ \minute.

\item Meanwhile, chop the basil, shred the cheese.

\ragmarpar{can also serve topped w/ ricotta}
\item Stir in the noodles, basil, cheese, cream.
	Simmer $\approx 2$ \minute.

\item Serve topped w/ basil and a glass of Chianti.
\end{preparation}


\begin{experiments}
\item The parmesan does not dissolve well, perhaps slices of asiago would work better?
\end{experiments}

\recipeend
