\section{Frijoles de Olla}\index{beans!Frijoles~de~Olla}\label{frijoles_de_olla}


\begin{recipestats}[
	servings=12 $C$,
	preptime=15 \minute,
	bakingtime=3 \hour,
	original=\citeauthor{miCocinaMartinez}~\cite[p.54]{miCocinaMartinez},
]
\end{recipestats}


\ragmarpar{Rick likes Avacado leaves for their cinnamon, allspice, \& citrus flavor.}
\begin{recipeabstract}
	Rick's simple and go-to bean recipe.
	Just throw in your vegatables and herbs and you're good to go.
	The key is to \textbf{not} soak the beans in water because if you do, they'll just taste like water.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][lb]{dried beans}\\
		\ingredient[16][C]{water}\\
		\ingredient[3][medium]{scallions}\\
		\ingredient[3][cloves]{garlic}
	\end{ingredientblock}

	\begin{ingredientblock}
		\ingredient[2][leaves]{avocado}\\
		\ingredient[3][sprigs]{epazote}\\
		\ingredient[17][g]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Fresh or dried herbs are ok.}
\begin{preparation}
	\item Rinse the beans and remove any debris.
	\item Lightly crush then peel the garlic, trim the scallions.
	\item Combine all in a pot, bring to a boil, reduce to a low simmer.
	\item Cook uncovered, skim \& stir occassionally.\\
		Check regularly that the beans are covered by water.
	\item Cook until the beans are tender $\approx[2.5\;..\; 3.5]$ \hour.
	\item Remove the garlic, scallions, herbs. Season to taste.
\end{preparation}


\ragmarpar{Refridgerate $\le2$ days, or freeze $\le3$ months.}
\begin{variation}
	\item Use Avacado or bay leaves, dried or fresh.
	\item Use fresh epazote or combine some parsely / oregano / mint.
\end{variation}


\recipeend%
