\section[Frijoles con Veneno]{Frijoles con Veneno, or\\Beans with Poison}\index{beans!Frijoles~con~Veneno}


\begin{recipestats}[
	servings=6,
	preptime=1 \hour,
	bakingtime=3 \hour,
	original=\citeauthor{miCocinaMartinez}~\cite[p.208]{miCocinaMartinez},
]
\end{recipestats}


\ragmarpar{``The only thing this veneno will kill is your hunger\cite{miCocinaMartinez}.''}
\begin{recipeabstract}
	Pork ribs braised in chiles on top of refried beans.
	The poison refers to the pork fat that is stained red by the dried chiles.
	Rick notes that this is a fine main dish even though it's a side, and recommends making taquitos.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[2][\Tablespoon]{lard}\\
		\ingredient[2\; \onefourth][\pound]{pork ribs}\\
		\ingredient[4][]{ancho}\\
		\ingredient[6][]{guajillo}\\
		\ingredient[8][cloves]{garlic}\\
		\ingredient[3][C]{orange juice}
	\end{ingredientblock}

	\begin{ingredientblock}
		\ingredient[12][g]{salt}\\
		\ingredient[1][\teaspoon]{cumin}\\
		\ingredient[1][\teaspoon]{oregano, Mexican}\\
		\ingredient[1][leaves]{bay}\\
		\ingredient[1][\Tablespoon]{apple cider vinegar}\\
		\ingredient[6][C]{\ref{frijoles_refritos}~\nameref{frijoles_refritos}}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Fresh juice is best, about 8 oranges.}
\begin{preparation}
	\item Preheat oven to 275 \Fahrenheit\ w/ a rack on the lower third.
	\item Rinse \& dry the chiles, remove stems \& seeds.
	\item Prepare the spices, press the oranges.
	\item Heat a large pot on medium high, add lard.
		Sear pork in batches until browned on all sides, $\approx8$ \minute.
		Transfer to a plate.
	\ragmarpar{Pinto beans are best.}
	\item Add chiles to the pot and toast $\approx[1..2]$ \minute, stirring frequently.
		Transfer to a plate.
	\item Add garlic and cook while stirring frequently $\approx1$ \minute.
		Add pork, chiles, juice, spices.
		Bring to a boil.
	\item Cover, transfer to oven, braise $\approx[2..2\;\onehalf]$ \hour.
	\item Transfer all meat to another bowl, discard bay leaves.
	\item Blend the chiles with an immersion blender until smooth.
	\item Shred the pork and discard the bones.
	\item Add pork to chile, add vinegar.
	\item Serve over refried beans with tostadas and tortillas.
\end{preparation}


\begin{experiments}
	\item Try blending chiles separately and discarding the water to reduce bitterness.
\end{experiments}
\recipeend%
