\section[Mushroom Wellington]{Mushroom Wellington}\index{mushroom!Mushroom Wellingto}\index{vegan!Mushroom Wellington}


\begin{recipestats}[
	servings=6,
	preptime=60~\minute,
	bakingtime=30~\minute,
	source=The Giesken Family,
	original=\citeauthor{mushroomWellingtonMalik}~\cite{mushroomWellingtonMalik},
]
\end{recipestats}

\begin{recipeabstract}
	A Giesken Christmas eve tradition.
	The Dijon really brings the dish together.
\end{recipeabstract}
\ragmarpar{Use two skillets.}


\begin{ingredientcolumns}
	\begin{ingredientblock}[filling]
		\ingredient[24][\ounce]{mushrooms}\\
		\ingredient[3][large]{white onion}\\
		\ingredient[3][\Tablespoon]{oil}\\
		\ingredient[300][g]{baby spinach}\\
		\ingredient[1][\teaspoon]{thyme}\\
		\ingredient[\approx16][\ounce]{vegan puff pastry}\\
		\ingredient[1][\Tablespoon]{Dijon}
	\end{ingredientblock}

	\begin{ingredientblock}[egg wash]
		\ingredient[1][\Tablespoon]{aquafaba}\\
		\ingredient[1][\Tablespoon]{nut milk}\\
		\ingredient[1][\Tablespoon]{oil}\\
		\ingredient[\onehalf][\teaspoon]{maple syrup}\\
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
	\item Reserve a large skillet and greased $\approx9\times13''$ dish or sheet.
	\item Halve and slice onions into strips along the axis.
	\item Caramelize the onions.
		Heat onions covered w/ dash of salt, oil, and $\approx~\onefourth~C$ hot water on medium until boiling.
		Heat until translucent, reduce to medium-low, remove lid, let water boil off, add oil, stir occasionally until well browned, $\approx30~\minute$.
	\ragmarpar{Parboiling decreases cook time.}
	\item Meanwhile, wash and slice the onions $\approx\onehalf''$ thick.
	\item Saut\'{e} the mushrooms.
		Heat mushrooms covered w/ dash of salt, oil, and $\approx~\onefourth~C$ hot water on high until boiling.
		Heat $\approx5~\minute$, reduce to medium, remove lid, let water boil off, add oil, stir occasionally until well browned.
	\item Saut\'{e} the spinach until wilted.
	\item Remove each when done and cool in the fridge.
	\item Preheat oven to $390~\Fahrenheit$.
	\item Line dish with parchement paper and add the pastry.
	\item Toss mushrooms with salt, pepper, thyme, Dijon.
	\item Add onions over the middle $\onethird$, leaving a $\approx\threefourth''$ border.
	\item Add layers of $\onehalf$ of spinach, mushrooms, $\onehalf$ spinach.
	\item Roll pastry into a log, seal edges, roll over w/ seam on bottom.
	\item Whisk egg wash ingredients and coat pastry, freeze $10~\minute$.\\
		Repeat wash / freeze cycle once more.
	\item Bake $[30..35]~\minute$, serve immediately.
\end{preparation}


\recipeend%
