\section[Smashed Potatoes]{Smashed Baby Potatoes}\index{potato!Smashed~Pototatoes}


\begin{recipestats}[
	servings=6,
	preptime=10~\minute,
	bakingtime=45~\minute,
	source=Pamela Teresi,
]
\end{recipestats}

\begin{recipeabstract}
	Potatoes both boiled and mashed.
	A fancy tater for a fancy meal.
\end{recipeabstract}


\ragmarpar{Waxy potatoes are best.}
\begin{ingredientcolumns}
	\columnbreak
	\begin{ingredientblock}[sauce]
		\ingredient[2][\Tablespoon]{butter}\\
		\ingredient[1][clove]{garlic}\\
		\ingredient[1][\Tablespoon]{olive oil}\\
		\ingredient[1][\Tablespoon]{parsely}\\
		\ingredient[2][\teaspoon]{thyme, fresh}\\
		\ingredient[1][\teaspoon]{rosemary, fresh}\\
		\ingredient[\onehalf][\teaspoon]{salt}\\
		\ingredient[4][turns]{black pepper}
	\end{ingredientblock}
	\begin{ingredientblock}[potatoes]
		\ingredient[2][\pound]{baby potatoes}\\
		\ingredient[4][sprig]{rosemary}\\
		\ingredient[3][clove]{garlic}\\
		\ingredient[\onefourth][C]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Fill a 3 $\quart$ pot about halfway, and begin to heat on high.
\item Preheat oven to 425 $\Fahrenheit$.
	Grease a large baking sheet.
\item Meanwhile clean potatoes, measure salt, chop thyme, rosemary, parsely.
\item Add salt, potatoes, rosemary springs, 3 smashed cloves, stir.
\item Add enough water to cover potatoes, bring to a boil.
\item Reduce to simmer and cook for $[10..15]$ \minute, drain, discard spices.
\item Move potatoes to baking sheet.
	Flatten each w/ a glass to $\approx \onehalf \inch$.
\item Brush with oil, bake 25 \minute.
\item Melt butter, crush garlic and mix all sauce ingredients.
\item Brush over potatoes, serve.
\end{preparation}


\recipeend%
