\section[Focaccia]{Handshake Focaccia~\vegan}


\index{bread!Focaccia}


\begin{recipestats}[
	servings=6 people,
	preptime=3 \hour,
	bakingtime=15 \minute,
	source=\citefield{howToBake2013}{title} \cite{howToBake2013},
	]
\end{recipestats}


\begin{recipeabstract}
	A Focaccia worthy of the Paul Hollywood Handshake.
	This is best eaten out of the oven and dipped in olive oil with a little salt and or-A-gaano (as they say in Britain).
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[500][\gram]{bread flour}\\
		\ingredient[10][\gram]{salt}\\
		\ingredient[10][\gram]{yeast, instant}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[140][\milliliter]{olive oil}\\
		\ingredient[360][\milliliter]{water}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Mix the dough.
	Add flour to mixing bowl, add salt \& yeast on opposite sides.
	Add 40 \milliliter~oil \& $\approx\threefourth$ water, hand mix.
	Continue mixing and gradually add water until all the flour is incorporated; water may be left over.
	Aim for a soft / wet dough.

\item Knead the dough.
	Add some oil to the working surface, then the dough.
	Knead $5 \dots 10$ \minute.
	Knead past the wet stage until the exterior is smooth \& soft.
	Refrain from adding more flour.

\item Rise the dough.
	Move it to a lightly oiled $\approx 2 \dots 3$ \quart~tub.
	Add tea towel on top, rise $\approx 1 \hour$ until at least doubled in size.

\item Separate the dough.
	Line baking parchment to two trays, drizzle olive oil on top.
	Add olive oil to the working surface, optionally dust w/ fine semolina.
	Move dough to working surface slowly as to keep air in the dough.
	Divide dough in half and stretch out flat onto the trays.

\item Prove the dough.
	Add each tray into a plastic bag and prove for $\approx 1$ \hour, until it has doubled in size.
	The dough should spring back quickly.
	Preheat oven to 430 \Fahrenheit.

\item Bake.
	Add dimples on top of the dough using your fingers; push all the way to the bottom.
	Drizzle each with olive oil, top with flaked salt and oregano.
	Bake $\approx 15$ \minute.
	The bread should be cooked through so that tapping the bottom will sound hollow.
	Drizzle with olive oil, cool.
\end{preparation}


\recipeend
