\section[Soft Pretzels]{Buttery Soft Pretzels}


\index{bread!Soft~Pretzels}


\begin{recipestats}[
	servings=8 pretzels,
	preptime=1\onehalf~\hour,
	bakingtime=20 \minute,
	source=\citefield{notChicken2019}{shorttitle} \cite{notChicken2019},
	vegetarian=vegan opt,
]
\end{recipestats}

\begin{recipeabstract}
	Buttery and soft indeed.
	Emma introduced us to these with vegan butter which worked very well.
\end{recipeabstract}

\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[3][\Tablespoon]{sugar}\\
		\ingredient[7][\gram]{yeast, active dry}\\
		\ingredient[1][C]{water}\\
		\ingredient[2 \onehalf][C]{flour, all purpose}\\
		\ingredient[2][\teaspoon]{malt powder}\\
		\ingredient[1][\Tablespoon]{butter}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[4][C]{water, hot}\\
		\ingredient[\onefourth][C]{baking soda}\\
		\ingredient[\approx 1][\Tablespoon]{pretzel salt}
	\end{ingredientblock}
\end{ingredientcolumns}

\ragmarpar{diastatic malt powder optional}
\begin{preparation}
\item Proof yeast in 1 $C$ water at $[105 \dots 115]$ \Fahrenheit~with sugar, 10 \minute.

\item Mix flour, malt, water, melted butter until combined.
	Knead on a floured surface $[3 \dots 5]$ \minute, form into ball.
	Grease a large bowl, add dough, cover w/ towl.
	Rise to double in size, $\approx 1$ \hour.

\item Punch down dough, remove from bowl and divide into 8 pieces.

\item Form each piece into pretzels.
	Roll out to $\approx 17"$.
	Twist ends together, fold over and affix ends to the center.

\item Preheat to 400 \Fahrenheit, line two baking sheets w/ parchment paper.

\item Bring the water to a light simmer and a medium pot.
	Stir in baking soda.
	For each pretzel, dip into bath for $\approx 5$ \second~using a spoon.
	Remove, place onto sheet, and immediately sprinkle with salt.

\item Bake $[12 \dots 15]$ \minute~or until the desired color is achieved.
	Cool 10 \minute, brush with additional melted butter to taste.
\end{preparation}

\recipeend
