\section{Stuffed Shells}\index{pasta!Stuffed Shells}


\begin{recipestats}[
	servings=12,
	preptime=2~\hour,
	bakingtime=25~\minute,
	source=Mike~\&~Jane,
	original=\citeauthor{raguseaStuffedShells}~\cite{raguseaStuffedShells},
]
\end{recipestats}


\ragmarpar{Jane likes this.}
\begin{recipeabstract}
	A stuffed shell that's perfect for freezer meal prep.
	Freeze up to 3 months.
	This recipe makes extra sauce which is useful for quick lunches.
	\end{recipeabstract}


\ragmarpar{That's four 28\ounce~cans.}
\begin{ingredientcolumns}
	\begin{ingredientblock}[sauce]
		\ingredient[2][]{onion}\\
		\ingredient[\approx\onefourth][C]{olive oil}\\
		\ingredient[8][clove]{garlic}\\
		\ingredient[6][\ounce]{tomato, paste}\\
		\ingredient[112][\ounce]{tomato, crushed}\\
		\ingredient[1][C]{Chianti}\\
		\ingredient[2][\Tablespoon]{butter}\\
		\ingredient[1][\Tablespoon]{sugar}\\
		\ingredient[\onehalf][\teaspoon]{salt}\\
		\ingredient[\onehalf][\teaspoon]{baking soda}\\
		\ingredient[1][C]{parsley}\\
		\ingredient[1][\Tablespoon]{basil}
	\end{ingredientblock}

	\begin{ingredientblock}[shells]
		\ingredient[1\onehalf][lb]{jumbo shells, dry}\\
		\ingredient[3][lb]{ricotta}\\
		\ingredient[1][lb]{mozzarella}\\
		\ingredient[1][lb]{spinach, frozen}\\
		\ingredient[8][\ounce]{pecorino}\\
		\ingredient[5][]{eggs}\\
		\ingredient[2][clove]{garlic}\\
		\ingredient[1][C]{parsley}\\
		\ingredient[\onehalf][\teaspoon]{black pepper}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Boil for baking may be $\approx 3$ $\minute$ less than al dente.}
\begin{preparation}
\item Reserve a large bowl, two pots, a $9~x~13"$ metal pan,\\
	$\approx$ five disposable $8.5~x~6"$ aluminum pans.
\item Gather sauce ingredients and one of the large pots.
\item Small dice the onion, crush the garlic, set each aside.
\item Measure the salt, sugar, baking soda, basil, butter.
\item Heat olive oil on medium, then add the onion.
\item Saut\'{e} until browned.
\item Meanwhile, open the cans, chop the parsley.
\item Add garlic \& butter, cook $1~\minute$, do not burn!
\ragmarpar{Save a little pecorino for serving.}
\item Add the tomato paste, cook $1~\minute$
\item Add the tomatoes to deglaze.
\item Add salt, sugar, soda, basil, parsley, Chianti.
\item Bring to a simmer, reduce to low, stir occasionally.
\ragmarpar{Lay shells out on sheet to prevent sticking.}
\item Preheat oven to $400~\Fahrenheit$.
\item Start heating salted water for the shells.
\item Gather the filling ingredients and a large bowl.
\item Drain the spinach, chop the parsley, shred the cheese.
\item Mix the cheese, ricotta, parsley, eggs, spinach, parsley.
\item Crush and mix the garlic.
\item Grease a baking pan and/or separate out the aluminum pans.
\item Boil the shells until pliable, $\approx$ 7 $\minute$, drain.
\item Toss with oil, separate shells that are stuck together.
\ragmarpar{The sauce should rise up $\approx~\onehalf$ way up the shells.}
\item Spread sauce into pan, fill shells and place cheese side up.
\item Cover with foil, bake 25 $\minute$, remove foil, broil briefly.
\item If freezing, add sauce, shells, cover, then freeze.
\ragmarpar{Seal pans in a bag to help it stay fesh.}
\item To reheat, remove paper lid, cover with foil.
\item Bake at 415 $\Fahrenheit$, for 75 $\minute$.
	Rotate halfway through.
\item Bake until the filling reaches 160 $\Fahrenheit$.
\item Remove foil, broil briefly.
\end{preparation}


\recipeend%
