\section[Chicken Soup]{Sunday Chicken Soup}


\begin{recipestats}[
	servings=8,
	preptime=1 \hour,
	bakingtime=2 \hour,
	source=Mike \& Jane,
]
\end{recipestats}


\ragmarpar{The roux kicks it up a notch, see \cite[p.~114]{ratioRuhlman} for tips.}
\begin{recipeabstract}
	A college tradition.
	Jane and I would get together Sunday in college for dinner,
		as she would get off work as a tutor and I would prepare meals for the week.
	I'd usually buy a whole chicken and roast it to cut down on cost,
		but we've since simplified and reduced the volume.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[50][g]{butter}\\
		\ingredient[50][g]{flour}\\
		\ingredient[\onehalf][]{onion, white}\\
		\ingredient[\onehalf][bunch]{celery}\\
		\ingredient[4][]{carrots}\\
		\ingredient[\approx~2][lb]{chicken thighs}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[1][]{leek}\\
		\ingredient[1][]{beer}\\
		\ingredient[2][lb]{chicken stock}\\
		\ingredient[\threehalf][\Tablespoon]{pastina}\\
		\ingredient[1][]{bay leaf}\\
		\ingredient[][]{season-all}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Use boneless, skinless thighs.}


\begin{preparation}
\item Prepare vegetables ahead of time.
	Cut the ends off the leak, slice in half lengthwise.
	Rinse and let soak in a bowl of water to remove the sand.

\item Dice the onion.
	Dice about and equal amount each of carrot and celery.
	Rangiri cut the carrots, medium dice the celery.

\item Chop the leak, discard upper half of the dark green section.

\ragmarpar{Lowry's or Saz\'on work well.}

\item Reserve a dutch oven, iron skillet, and wooden spoon.

\item Remove any bone fragments from the chicken, add seasoning.

\item Measure the butter and flour.

\item Heat skillet on medium w/ oil, heat pot on medium low.

\ragmarpar{Butter is ready if it starts to brown.}
\item Heat butter to evaporate the water $\approx2$ \minute.

\item Add flour, stir $\approx 15$ $\minute$ until you reach a blonde roux the color of a pale ale ($\approx$ SRM 10).

\item Meanwhile, cook the chicken thighs until browned.
\ragmarpar{Use a splatter screen w/ the skillet.}

\item Add mirepoix and a dash of salt to roux.
	Cook $\approx 10$ $\minute$, de-glaze with beer, add stock and an equal part of water.

\item Bring to a boil, then reduce to a light simmer, add bay leaf.

\item Remove chicken when it reaches $\approx 175$ $\Fahrenheit$.
	Deglaze with beer, scrape the fond, add to soup.
	Cut the chicken, add.

\item Stew $\approx 1$ $\hour$.

\item Add carrots $\approx 15$ $\minute$ before serving.

\item Add leaks and celery $\approx 10$ $\minute$ before serving.

\item Add pastina $\approx 5$ $\minute$ before serving.

\item Season to taste and serve.
\end{preparation}


\recipeend%
