\section[Cioppino]{Mom's Cioppino}\index{shellfish!Cioppino}\index{fish!Cioppino}
\ragmarpar{Chuh-pee-no.}


\begin{recipestats}[
	servings=6,
	preptime=45 \minute,
	bakingtime=1 \hour,
	source=Pamela Teresi,
]
\end{recipestats}


\ragmarpar{Inspired by Jenn Segal, Giada de Laurentis, Ina Garten et. al.}
\begin{recipeabstract}
	An Italian-American fish soup hailing from San Francisco.
	Combine your selection of fish, shellfish, tomoatoes and wine, serve with sourdough.
	A favorite of Pam and Scott during the holidays.
	Also known as Fisherman's Stew.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][\pound]{cod}\\
		\ingredient[1\onehalf][\pound]{shrimp, raw}\\
		\ingredient[1][\pound]{sea scallops}\\
		\ingredient[28][\ounce]{crushed tomato}\\
		\ingredient[4][\Tablespoon]{tomato paste}\\
		\ingredient[4][C]{chicken stock}\\
		\ingredient[1][C]{clam juice}\\
		\ingredient[1][C]{wine, dry white}\\
		\ingredient[\onefourth][C]{olive oil}\\
		\ingredient[3][\Tablespoon]{butter}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[1][C]{onion, yellow}\\
		\ingredient[3][]{shallots}\\
		\ingredient[3][clove]{garlic}\\
		\ingredient[7][sprig]{thyme}\\
		\ingredient[1][\teaspoon]{thyme, chopped}\\
		\ingredient[\threefourth][\teaspoon]{pepper flakes}\\
		\ingredient[\onehalf][\teaspoon]{oregano}\\
		\ingredient[2][\teaspoon]{sugar}\\
		\ingredient[1][\teaspoon]{salt}\\
		\ingredient[1][]{baguette}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Use fresh thyme.}


\begin{preparation}
\item Reserve a large soup pan.

\item Pick and rinse the thyme, chop.

\item Dice the onion, shallot, crush the garlic.

\item Heat oil on medium, saut\'{e} onion \& shallots $\approx[5..10]$ $\minute$.

\ragmarpar{Halibut also works.}
\item Add garlic, cook $\approx[1..2]$ $\minute$, do not brown.

\item Add wine, increase to high heat, reduce by half $\approx[3..4]$ $\minute$.

\item Add crushed tomatoes, clam juice, stock, salt, pepper flakes, oregano, thyme sprigs, tomatoe paste.

\item Bring to a boil, reduce heat, simmer 25 \minute.

\item Meanwhile peel and deveine shrimp.
	Cut fish into $\approx2$ $\inch$ pieces.
	Chop scallops in half crosswise.

\item When simmer is done remove thyme sprigs, add butter.

\item Gently sir in fish, shrimp, scallops.\\
	Simmer on low until fish is cooked through.

\ragmarpar{Clams and mussels are usually in Cioppino, but I have not used them.}
\item Season to taste with salt and pepper flakes.

\item Serve with garlic bread or baguette.
\end{preparation}


\begin{variation}
\item I've often seen diced fennel bulb and/or fennel seed.
	Add $\approx2$ $C$ fennel to the onions, add $1$ $\teaspoon$ seed w/ the garlic.

\item Crab is usually used in San Francisco, and I have occasionally used a can of pasteurized crab. Crab legs are more authentic.

\end{variation}

\recipeend%
