\section[Turkey Gumbo]{Thanksgiving Turkey Gumbo}\index{turkey!Turkey~Gumbo}


\begin{recipestats}[
	servings=[4 \ldots 6] people,
	preptime=45~\minute,
	bakingtime=4~\hour,
	source=Teresi Family,
]
\end{recipestats}


\begin{recipeabstract}
	A Teresi tradition; Scott says it is ``the best part of Thanksgiving.''
	Create a stock with the turkey bones for some extra pizazz.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[12][\ounce]{Andoullie sausage}\\
		\ingredient[3][C]{turkey}\\
		\ingredient[\onefourth][C]{butter}\\
		\ingredient[55][\gram]{flour}\\
		\ingredient[\nicefrac{3}{2}][C]{white onions}\\
		\ingredient[\nicefrac{3}{2}][C]{celery}\\
		\ingredient[1][C]{green bell pepper}\\
		\ingredient[4][C]{stock}\\
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[2][]{bay leaf}\\
		\ingredient[2][tsp]{white pepper}\\
		\ingredient[2][tsp]{marjoram}\\
		\ingredient[1][tsp]{salt}\\
		\ingredient[2][dash]{Tabasco}\\
		\ingredient[2][tsp]{gumbo fil\'{e}}\\
		\ingredient[1][C]{white rice}
	\end{ingredientblock}
\end{ingredientcolumns}

% TODO add garlic

\begin{preparation}
\item Reserve a dutch oven and skillet.

\item Dice vegetables; rangiri cut the sausage; measure butter, flour.

\item Make the roux.
	Melt the butter over medium heat $\approx 5$ \minute.

\item Increase heat to medium-high.
	Add flour, stirring constantly $\approx 20 \ldots 25$ $\minute$ until the color of peanut butter.

\item Add celery, onions, salt; cook $\approx 10$ \minute; deglaze w/ beer.

\item Meanwhile lightly brown the sausage and dice the turkey.

\item Add stock, turkey, sausage, bay leaf, salt, pepper, marjoram.

\item Simmer $\approx 4$ \hour.

\item Prepare rice to serve when gumbo is complete.
\ragmarpar{Serve w/ Ciabatta.}

\item Add Tabasco, salt to taste.

\item Add gumbo fil\'{e}, serve with rice.
\end{preparation}


\recipeend%
