\section[Hearty Italian]{Hearty Italian Sausage Soup}\index{sausage!Hearty~Italian~Soup}


\begin{recipestats}[
	servings=8,
	preptime=30 \minute,
	bakingtime=45 \minute,
	source=Pamela Teresi,
]
\end{recipestats}


\begin{recipeabstract}
	An easy and well rounded soup.
	The use of canned ingredients reduces preparation effort.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][\pound]{Italian sausage}\\
		\ingredient[1][large]{onion, white}\\
		\ingredient[2][clove]{garlic}\\
		\ingredient[1][\Tablespoon]{tomato paste}\\
		\ingredient[1][\Tablespoon]{oil, olive}\\
		\ingredient[29][\ounce]{stock, chicken}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[14.5][\ounce]{cannellini beans}\\
		\ingredient[14.5][\ounce]{tomatoes, crushed}\\
		\ingredient[14.5][\ounce]{potatoes, diced}\\
		\ingredient[1 \onehalf][C]{spinach, fresh}\\
		\ingredient[\onehalf][C]{parmasan}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{$14.5 \ounce$~is the standard can weight.}
\begin{preparation}
\item Reserve a $\ge 3.5$ $quart$ pot.
	Chop the onion, smash \& peel the garlic, drain the beans, shred the cheese.

\item Brown $\approx \onehalf$ the sausage, breaking it up as you go.
	Deglaze and add the onion and remaining sausage.
	Cook 10 \minute, breaking up the sausage and deglazing occasionally.

\item Stir in tomato paste, oil, crushed garlic, and cook $\approx$ 2 \minute.

\item Add stock, beans, tomatoes, and bring to a boil.
	Reduce heat and let simmer $\approx$ 30 \minute.

\item Drain and add the potatoes.
	Season to taste, optionally add basil / chili flakes.

\item Roughly chop the spinach and stir in.
	Remove form heat, cover, and rest $\approx 5$ \minute.
	Serve w/ cheese.
\end{preparation}


\begin{variation}
\item Sweet / mild / hot italian sausage all work.

\item Substitute mozarella etc. for parmesan; pasta for potatoes.
\end{variation}


\recipeend
