\section[Roux]{Roux}


\begin{recipestats}[
	bakingtime=30~\minute,
	original=\citetitle{ratioRuhlman}~\cite[p.~113]{ratioRuhlman},
]
\end{recipestats}


\begin{recipeabstract}
	Flour cooked in fat used to thicken soups and sauce.
	Color ranges from white, to blond, brown, then dark.
	A dark roux provides more flavor but has about half the thickening power\cite{ratioRuhlman}.
	Ruhlman's recipe is a ratio by weight.
	He recommends clarified butter or lard as oil won't provide a good flavor.
	A 1:1 ratio of regular butter can be used, but one should cook it first to remove some of the water, otherwise the thickening power is reduced.
\end{recipeabstract}


\ragmarpar{Ratio is by weight, not volume.}
\begin{ingredientcolumns}
	\begin{ingredientblock}[roux]
		\ingredient[3][parts]{fat}\\
		\ingredient[2][parts]{flour}
	\end{ingredientblock}

	\begin{ingredientblock}[thickening]
		\ingredient[10][parts]{liquid}\\
		\ingredient[1][parts]{roux}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Reserve a wooden spatula, and a metal whisk if you want.
\ragmarpar{Do not walk away from the pot!}
\item Measure your ingredients.
\item Melt your fat on medium high, add the flour and whisk in, reduce to medium low or low.
\item Stir constantly and do not walk away from the pot.
\ragmarpar{Butter may brown a little.}
\item Cook $\approx$ $[3..5]$ $\minute$ or until it smells like a pie crust.
\item Continue to cook to the desired color, remove from heat.
\item Whisk a cold roux into hot soup or cold soup into hot roux.
\item Cook $[20..30)$ $\minute$, stirring regularly, until smooth.
\ragmarpar{If you see black specks, or it smells burned, you will need to start again.}
\end{preparation}


\begin{variation}

\item Various fats\cite{wikiOilSmokePoint} and flavors are available.
	\begin{center}
	\begin{tabular}{l r l l}
		       & time                 & color \\ \midrule
		white  & $[3..5]$     \minute & pilsner\\
		blonde & $[5..10]$    \minute & pale ale\\
		brown  & $[20..25]$   \minute & amber ale\\
		dark   & $[30..45]$   \minute & brown ale\\
	\end{tabular}
	\end{center}
\ragmarpar{Don't use butter for a dark roux, it will burn.}
	\begin{center}
	\begin{tabular}{l r r}
		&
		\multicolumn{2}{c}{Smoke Point}\\
		\midrule
		butter            & $302~\Fahrenheit$ & $150~\Celsius$ \\
		clarified butter  & $482~\Fahrenheit$ & $250~\Celsius$ \\
		corn oil          & $446~\Fahrenheit$ & $230~\Celsius$ \\
		lard              & $374~\Fahrenheit$ & $190~\Celsius$ \\
		peanut oil        & $450~\Fahrenheit$ & $232~\Celsius$ \\
		vegetable oil     & $428~\Fahrenheit$ & $220~\Celsius$
	\end{tabular}
	\end{center}
\end{variation}


\recipeend%
