\section{Cacciannanze}%\index{bread!Cacciannanze}


\ragmarpar{cach-ee-ahn-NAHN-zeh}
\begin{recipestats}[
    servings=12,
    preptime=45~\minute,
    bakingtime=20~\minute,
    inactivetime=3~\hour,
    original=\citefield{caraccioloPizza}{shorttitle}~\cite{caraccioloPizza},
]
\end{recipestats}


\begin{recipeabstract}
    A quick and easy garlic and rosemary focaccia.
    \citeauthor{caraccioloPizza} provides many doughs, preparation methods, and focaccia recipes.
    This uses the 'quick' \cite[p.~83]{caraccioloPizza} dough with the stand mixer method,
    and is paired with the Cacciannanze \cite[p.~178]{caraccioloPizza} recipe.
    We like it for it's simple method and strong garlic flavor.
\end{recipeabstract}


\ragmarpar{10 \gram~if instant yeast.}
\begin{ingredientcolumns}
    \begin{ingredientblock}[dough]
        \ingredient[12][g]{active dry yeast}\\
        \ingredient[450][g]{water}\\
        \ingredient[350][g]{four, all-purpose}\\
        \ingredient[350][g]{four, bread}\\
        \ingredient[8][g]{sugar}\\
        \ingredient[70][g]{olive oil}\\
        \ingredient[17][g]{salt}
    \end{ingredientblock}
    \begin{ingredientblock}[topping]
        \ingredient[3][clove]{garlic}\\
        \ingredient[\approx~8][\teaspoon]{lard}\\
        \ingredient[][]{olive oil}\\
        \ingredient[][]{rosemary}\\
        \ingredient[][]{salt}
    \end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
    \ragmarpar{Don't knock out the air when spreading!}
\item Reserve a stand mixer, mixing bowl, large bowl, and a baking sheet $\approx 16~x~12$ $\inch$.
    Grease the sheet and large bowl.
\item Heat water to $[105..115]$ $\Fahrenheit$ and move to the mixing bowl.
\item Proof the yeast in the water with a dash of sugar for 5 $\minute$.
\item Measure salt, set aside. Mix the flours \& sugar.
\item Add flour mix to bowl, mix on low 5 \minute, rest 15 $\minute$.
\item Add salt \& oil, mix on low 5 $\minute$, rest 15 $\minute$.
    \ragmarpar{Grind dry rosemary in a mill.}
\item Mix on high until it sticks to the dough hook and doesn't tear when pulled from the side.
\item Transfer to a large bowl, cover w/ plastic wrap, rise 1 \hour.
\item Thinly slice the garlic, toss w/ a dash of salt \& rosemary.
    \ragmarpar{Original recipe is 18x13 \inch, $[15..20]$ $\minute$.}
\item Transfer dough to sheet, gently spread into an oval.\\
    If it doesn't spread then let rise $\approx~15$ \minute, try again.
\item Cover \& rise 1 \hour. Press garlic into the dough, rise 30 $\minute$.
\item Sprinkle rosemary and lard on top.
\item Preheat to 390 $\Fahrenheit$, bake $[20..25]$ $\minute$, rotating halfway through.
\item Let cool, lightly salt, serve with oil \& herbs.
\end{preparation}


\recipeend%
