\section[Brined Hot Sauce]{Base Brined Hot Sauce}

\label{base_lacto_brine_hotsauce}


\begin{recipestats}[
	servings=12 \fluidounce,
	preptime=1 \hour,
	bakingtime=2 \week,
	source=\citefield{fieryferments2017}{title} \cite{fieryferments2017},
	vegetarian=vegan,
	]
\end{recipestats}


\begin{recipeabstract}
	A base hot sauce recipe with whole brined peppers.
	Select your peppers, spices and other accouterments.
	Peppers are fermented whole and then pur\`{e}ed rather than mashed prior to fermentation, see ``Mixed-Media Basic Mash'' \cite{fieryferments2017}.
\end{recipeabstract}


\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[1][32~\fluidounce]{mason jar}\\
		\ingredient[1]{pickling weight}\\
		\ingredient[1]{air lock}\\
		\ingredient[\approx \onefourth][\fluidounce]{Star San}\\
		\ingredient[\approx48][\fluidounce]{water, un-chlorinated}\\
		\ingredient[\approx70][g]{salt, un-iodized}\\
		\ingredient[\approx8][\ounce]{peppers, fresh $\|$ dried}\\
		\ingredient{spices}\\
		\ingredient[\approx\onefourth][\teaspoon]{achiote}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Sanitize equipement with Star San or equivalent.

\item Prepare a $[5 \dots 5.3]\%$ brine by weight, $\approx\threefourth$ volume of jar.

\item Prepare dried peppers by removing stems, veins, and seeds. Keep flesh largely intact by slicing stem off and cutting once down length-wise, then unrolling the pepper.

\item Prepare fresh peppers by removing stems / seeds and cutting into large portions.

\item Add ingredients to jar.
	Prevent ingredients from floating up by starting with smaller pieces, then top off with a large dried pepper or cabbage leaf tucked down the sides of the jar.
	Reserve Achiote for post fermentation.

\item Add a fermentation weight to top of ingredients.

\item Add brine mixture, leaving $\approx1cm$ of head space.
	Remove ingredients floating on top of brine.

\item Add lid and air lock, making sure the lock vent is not covered in brine.

\item Ferment for $[1...2]$ \week~or up to many months, then place in fridge until ready to pur\`{e}e.
	Make certain that everything is covered in brine.

\item Separate brine and ingredients, pur\`{e}e with $\approx\onehalf$ $C$ brine.
	Strain if desired; recommended if dried peppers are used.
	Optionally blend Achiote for color.

\item Add vinegar or brine to desired consistency, refridgerate.
\end{preparation}


\begin{experiments}
\item Prevent spoilage by keeping ingredients submerged and by not removing the lid (keep it anaerobic).
	See \citefield{fieryferments2017}{title} \cite{fieryferments2017},
for troubleshooting.
	In general: you should throw out the batch if you see any fuzzy mold.
\item The heat level of the sauce lowers drastically over fermentation.
	Consider compensating for example with Thai, Pequin, or Arbol.
\item This recipe should probably have some cabbage in order to jump-start fermentation.
\end{experiments}


\recipeend
