\section{Falafel}\index{chickpeas!Falafel}


\begin{recipestats}[
	servings=8,
	preptime=30 \minute,
	bakingtime=30 \minute,
	inactivetime=25 \hour,
	source=Mike~\&~Jane,
	original=\citeauthor{falafelLisaBryan}~\cite{falafelLisaBryan},
]
\end{recipestats}

\begin{recipeabstract}
	We tried Falafel for a healthy Mediterranean bowl.
	It works well both fried and baked in a bowl, tacos, and pita.
	The garlic confit really takes it up a notch.
\end{recipeabstract}
\ragmarpar{Canned chickpeas not recommended.}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1~\onehalf][C]{chickpeas, dry}\\
		\ingredient[\approx~24][\fluidounce]{frying oil}\\
		\ingredient[\onehalf][]{onion}\\
		\ingredient[1][]{poblano}\\
		\ingredient[1][]{jalepe\~{n}o}\\
		\ingredient[\onehalf][bunch]{parsley}\\
		\ingredient[3][clove]{garlic}\\
		\ingredient[1][\Tablespoon]{garlic confit}\\
		\ingredient[3][\teaspoon]{cornstarch}\\
		\ingredient[1][\teaspoon]{baking powder}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[2][\teaspoon]{cumin}\\
		\ingredient[1][\teaspoon]{fennel}\\
		\ingredient[1][\teaspoon]{sage}\\
		\ingredient[3][pods]{cardamom}\\
		\ingredient[1][\teaspoon]{pepper}\\
		\ingredient[1][\teaspoon]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Soak beans w/ 1 $\teaspoon$ baking soda to soften.}
\begin{preparation}
\item Prepare the garlic confit ahead of time, use within 2 $\week$.

\item Soak dry chickpeas 24 $\hour$ ahead, with plenty of water.

\item Reserve a food processor, a pot or skillet, and cooking oil.

\item Grind the spices, roughly chop the vegetables, smash the garlic.

\item Drain the chickpeas and blend in batches. Aim for a slightly coarse mixture, not as fine as sand.

\item Blend into a batch the cornstarch, baking powder, garlic confit.

\item Blend the vegetables and herbs. Mix all in a large bowl.

\item Refrigerate $\approx [30 .. 60]$ $\minute$.

\item Heat oil in a pot to $\approx 350~\Fahrenheit$.

\item Scoop out mixture with two spoons into oblong balls, set aside.
\ragmarpar{Don't fry too many at once, they won't cook.}

\item Fry in the oil in batches until toasted.

\end{preparation}


\begin{variation}
\item Alternatively bake patties at 400 $\Fahrenheit$ for $\approx 15$ $\minute$ on a well oiled sheet, flipping halfway through.

\end{variation}


\recipeend%
