\section{Hoola Poola}\index{Spam!Hoola~Poola}\index{collards!Hoola~Poola}


\begin{recipestats}[
	servings=1 person,
	preptime=10 \minute,
	bakingtime=20 \minute,
	source=Mike,
	]
\end{recipestats}


\ragmarpar{Saz\'on is an all purpose seasoning often made with cumin \& coriander.}
\begin{recipeabstract}
	A cost-effective lunch.
	The ingredients keep a long time and can mostly be prepared before hand.
	The name is a play on the Giesken's balogna \& eggs recipe Hunka Punka. % FUTURE add ref to Hunka Punka
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[4][\ounce]{Spam}\\
		\ingredient[2][C]{collards}\\
		\ingredient[1][C]{chickpeas, cooked}\\
		\ingredient[1][C]{rice, cooked}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\approx~\onehalf][\teaspoon]{saz\'on}\\
		\ingredient[1][\Tablespoon]{butter}\\
		\ingredient[\onehalf][\Tablespoon]{garlic, minced}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{GOYA saz\'on w/ annato works well, other seasonings are available.}
\begin{preparation}
\item Dice and add Spam to frying pan over medium heat.
	Optionally add mushrooms, or other customization.
	Stir occasionally.

\item Meanwhile prepare the collards.
	Discard woody stems, slice leaves to $\approx1\times1''$, let soak in water w/ a dash of vinegar and salt.
	Set aside remaining ingredients.

\item Once Spam is toasted, drain majority of water from collards, add to pan, add Saz\'on.
	Stir often and cook until collards begin to get crispy.

\item Once collards are toasted, reduce heat a bit, expose center of pan by pushing mixture aside and add butter and garlic.
	Cook to a light toast ($\approx[30..60]$ \second).

\item Serve with rice.
	Top with a dash of Saz\'on and yell ``HOOLA POOLA!'' for a bit of pizzazz.
\end{preparation}


\recipeend%
