\section[Kraut Runza]{Kraut Runza}\index{beef!Kraut~Runza}


\begin{recipestats}[
	servings=8,
	preptime=30~\minute,
	bakingtime=4~\hour,
    original=Mrs. Sheck \& Mrs. Steinmiller,
]
\end{recipestats}


\ragmarpar{We usually use about $[1\onehalf .. 2]$ $\pound$ beef.}
\begin{recipeabstract}
    A Teresi Christmas tradition.
    Runza is a yeast roll filled with beef, cabbage, and plenty of pepper.
    Straight from Leah Scheck (Oma's aunt) and Mary Katherine Steinmiller (Oma's grandma).
    It is a German / Russian dish that is a specialty of Nebraska, where my mother's side of the family are from.
    The dish is also called ``Bierocks'', and they called it a ``Kraut'' Runza as they were of German descent.
\end{recipeabstract}


\begin{ingredientcolumns}
    \begin{ingredientblock}
		\ingredient[1][\pound]{ground beef}\\
        \ingredient[3][large]{onion, white}\\
        \ingredient[2][\pound]{cabbage}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[][]{white bread dough}\\
        \ingredient[][]{salt \& pepper}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\ragmarpar{Use an egg wash before baking.}
\item Reserve a large saut\'{e} pan, chop the onion and cabbage.
\item Brown the beef, add chopped onion and cabbage, season with salt \& pepper, cook slowly.
\item Make white bread dough.
\ragmarpar{Use a lot of freshly ground black pepper.}
\item Roll out to $\onefourth$ $\inch$ thickness, cut in squares $\approx6x6$ or $7x7$ $\inch$.
    You can make them any size you want.
\item Put in filling \& bake at $[375..400]$ $\Fahrenheit$, about 30 $\minute$ until dough is brown.
\end{preparation}


\recipeend%
