\section[Linguine Broccoli]{Linguine with Broccoli-Mint Pesto}\index{pasta!Linguine~Broccoli}\index{broccoli!Linguine~Broccoli}\index{pesto!Linguine~Broccoli}


\begin{recipestats}[
	servings=6,
	preptime=30~\minute,
	bakingtime=30~\minute,
	source=Mike \& Jane,
	original=\citefield{realSimple2023LinguinePesto}{journaltitle}~\cite{realSimple2023LinguinePesto},
]
\end{recipestats}


\begin{recipeabstract}
	A mostly healthy broccoli delivery mechanism.
\end{recipeabstract}
\bigskip  % NB added to get the ingredients to stay on one page, update as necessary
% FUTURE how can we force a twocol to not span more than 1 page?


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[5][\ounce]{broccoli}\\
		\ingredient[1][\pound]{linguine}\\
		\ingredient[\onehalf][C]{almonds}\\
		\ingredient[1 \onehalf][C]{basil leaves}\\
		\ingredient[\onehalf][C]{mint leaves}
	\end{ingredientblock}

	\bigskip
	\begin{ingredientblock}
		\ingredient[2][\ounce]{pecorino}\\
		\ingredient[2][clove]{garlic}\\
		\ingredient[1][\teaspoon]{salt}\\
		\ingredient[1][C]{olive oil}\\
		\ingredient[1][]{lemon}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Measure broccoli, almonds, grate the cheese, pick and rinse the herbs, smash garlic.
\ragmarpar{Mike \& Jane like this for the basil.}
\item Bring large pot of water to a boil, generously salt.
\item Boil broccoli $\approx3$ $\minute$, until just tender, transfer to plate.
\item Return to a boil, cook pasta according to package.
	Reserve 1 $C$ pasta water, drain and return to pot.
\item Meanwhile add almonds to food processor, pulse to a fine chop.
\item Add basil, mint, cheese, garlic, salt.
	Pulse $\approx$ $30$ $\second$.
\item Add broccoli, pulse until combined.
\item Add oil slowly while running processor, process until smooth.
\item Add pesto and $\approx$ $\onehalf$ $C$ water to pot.
	Toss to coat pasta.
	Add water to desired consistency.
\ragmarpar{Add the salt and say ``Bam!''}
\item Plate pasta, add lemon wedge, top with oil, basil or mint, pecorino.
\item Serve, squeeze a little lemon juice on top, add flakey salt.
\end{preparation}


\recipeend%
