\section[Spinach Quiche]{Spinach Artichoke Quiche}\index{egg!Spinach~Quiche}\index{quiche!Spinach~Quiche}


\begin{recipestats}[
	servings=4 people,
	preptime=45 \minute,
	bakingtime=45 \minute,
	source=Mike \& Jane,
	original=\citefield{joyofcooking2006}{title}~\cite{joyofcooking2006},
	]
\end{recipestats}


\begin{recipeabstract}
	A classic dish.
	We like to serve this as a side along with cardamom rice and have leftovers for breakfast.
\end{recipeabstract}
\ragmarpar{See~\ref{basicFlakyPiePastry} for pastry recipe.}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][]{pie pastry}\\
		\ingredient[5][large]{eggs}\\
		\ingredient[1][C]{cream}\\
		\ingredient[2\;\onehalf][C]{spinach}\\
		\ingredient[4][\ounce]{Asiago}\\
		\ingredient[6][\fluidounce]{artichokes}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[1][]{onion, white}\\
		\ingredient[3][Tbs]{butter}\\
		\ingredient[2][\teaspoon]{garlic}\\
		\ingredient[\onefourth][\teaspoon]{salt}\\
		\ingredient[\onehalf][\teaspoon]{pepper, white}\\
		\ingredient[\onehalf][\teaspoon]{marjoram}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Prepare pastry ahead of time and chill.\\
	If using a premade crust, let it soften.

\item Reserve a bowl, saut\'{e} pan, and a pie plate. Butter the plate.

\item Preheat oven to $400$ \Fahrenheit.

\item Slice onion, cook over medium-low heat with a little olive oil while stirring occasionally.

\item Measure spinach, artichokes. Grind salt, pepper, marjoram.

\ragmarpar{See~\ref{basicFlakyPiePastry} for more partial prebake details.}
\item Add and shape pastry to the pan, pre-bake for 15 $\minute$ @ $400\;\Fahrenheit$ w/ weights, $[10..12]$  $\minute$ @ $375\;\Fahrenheit$ w/o weights.

\item Meanwhile, roughly chop artichokes \& spinach, shred cheese.

\item Add spinach to onions.
	Add garlic, butter, and cook $\approx 1$ \minute, take off the heat.

\item Combine remaining eggs, cream, salt, pepper, marjoram.

\item Layer into pie: cheese, vegetables, eggs.\\
	Optionally garnish with $\onehalf$ $\teaspoon$ paprika for some pizzazz.

\ragmarpar{Check at $20~\minute$ \& add foil to edges if needed to prevent burning.}
\item Bake at $375$ \Fahrenheit~for $30$ \minute, broil briefly, rest $10$ \minute.
\end{preparation}


\begin{variation}
\item Quiche Lorraine uses bacon and Gruyere, quiche Florentine is spinach and Gruyere, and leek and onion appear popular.

\item Other milk varieties are available, but heavy cream is recommended.
\end{variation}

\begin{experiments}
\item Try cheddar or romano, asiago sometimes has an off flavor.
\end{experiments}


\recipeend%
