\section{Banana Pancakes}\index{banana!Banana~Pancake}


\begin{recipestats}[
	servings=12 pancakes,
	preptime=10 \minute,
	source=Mike \& Jane,
]
\end{recipestats}

\ragmarpar{About 2 bananas.}
\begin{recipeabstract}
	A breakfast to make on the weekend after sleeping in.
	Save your ripe bananas in the freezer so that you're always prepared.
	We like to serve these with jam.
\end{recipeabstract}
\ragmarpar{Mike likes apricot, Jane likes Blackberry.}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][C]{flour, all-purpose}\\
		\ingredient[2][\Tablespoon]{sugar}\\
		\ingredient[2][\teaspoon]{baking powder}\\
		\ingredient[1]{\teaspoon}{vanilla}\\
		\ingredient[\onehalf][\teaspoon]{salt}
	\end{ingredientblock}

	\begin{ingredientblock}
		\ingredient[\onehalf][C]{Greek yogurt}\\
		\ingredient[\onehalf][C]{milk, whole}\\
		\ingredient[\approx7..9][\ounce]{banana, ripe}\\
		\ingredient[1]{egg}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Cut ends off frozen banana then once lengthwise, peel.}
\begin{preparation}
\item Mix flour, sugar, baking powder, salt, set aside.

\item Begin to preheat your pan on medium low to medium.

\item Peel bananas into a large bowl, mash briefly with fork.

\item Mix in yogurt, egg, milk, beat with fork.

\item Fold in the flour to the banana mixture until just combined.

\item Butter the skillet, add two spoonfuls of batter per each cake.
	Cook on first side until bubbles come through.
	Flip and cook until lightly brown, $\approx2$ \minute.
\ragmarpar{An iron skillet is best.}

\item Adjust heat after each batch if necessary, repeat.

\item Serve w/ syrup and apricot or strawberry jam.
\end{preparation}


\recipeend%
