\section{Cinnamon Rolls}\index{cinnamon!Cinnamon Rolls}


\begin{recipestats}[
	servings=16,
	preptime=1,
	bakingtime=cook time,
	inactivetime=12 \hour,
	source=Jane \& Mike,
	original=\citetitle{joyofcooking2006}~\cite[p.~621]{joyofcooking2006},
]
\end{recipestats}
\ragmarpar{Mike likes to use piloncillo.}


\begin{recipeabstract}
	Jane's favorite and a Christmas tradition.
	Make the dough ahead of time and let rise overnight.
	Cut the discs thick and let rise to decent size.
	Jane likes the cream cheese frosting, Mike prefers a simple sugar glaze.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}[dough]
		\ingredient[\onefourth][C]{water}\\
		\ingredient[2\onefourth][\teaspoon]{yeast, active}\\
		\ingredient[1][\teaspoon]{sugar}\\
		\ingredient[\onethird][C]{sugar}\\
		\ingredient[\onefourth][C]{milk}\\
		\ingredient[2][]{eggs}\\
		\ingredient[1][\teaspoon]{salt}\\
		\ingredient[1][\teaspoon]{vanilla}\\
		\ingredient[6][\Tablespoon]{butter}\\
		\ingredient[2\threefourth][C]{flour}
	\end{ingredientblock}

	\columnbreak
	\begin{ingredientblock}[filling]
        \ingredient[1][C]{brown sugar}\\
		\ingredient[\onefourth][C]{butter}\\
		\ingredient[1\onehalf][\Tablespoon]{cinnamon}\\
		\ingredient[8][pods]{cardamom}
	\end{ingredientblock}

	\medskip
	\begin{ingredientblock}[frosting]
		\ingredient[4][\ounce]{cream cheese}\\
		\ingredient[3][\Tablespoon]{butter}\\
		\ingredient[\threefourth][C]{powdered sugar}\\
		\ingredient[\onehalf][\teaspoon]{vanilla}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\ragmarpar{Knead in butter for 10~\minute, if by hand.}
\item Reserve a large bowl, mixer, and $\approx~2$ $\hour$ of preparation time.
\item Let butter soften and grease the bowl.
\item Heat water to $[105 .. 115]$ $\Fahrenheit$.
	Add to the mixer the yeast, a little sugar; let stand 5 $\minute$.
\item Mix in slowly: $\onehalf$ $C$ flour, sugar, milk, eggs, vanilla, salt.
\item Mix remaining flour in slowly, kneed 1 $\minute$.
\ragmarpar{Add 1 $\teaspoon$ cornstarch and water to the filling.}
\item Knead in butter $[5 .. 7]$ $\minute$, or until smooth.
\item Move to the bowl, cover, let rise $\approx1~\onehalf$ $\hour$, or until doubled.
\item Punch down and knead briefly, refrigerate $\approx4..12$ $\hour$.
\item Take the butter out to soften.
\item Grind cardamom, add filling ingredients to a bowl.
\ragmarpar{Add a bit of nutmeg.}
\item Roll the dough out $\approx1~cm$ thick.
\item Microwave filling on low until butter is very soft, mix well.
\item Spread filling on the dough, leave $\approx$ 1 $\inch$ clear on the top.
\item Roll into a cylinder, slice $\approx1$ $\inch$ thick.
\item Move to a greased pan and cover.
	Let rise $[30..60]$ $\minute$.
\item Bake at 350 $\Fahrenheit$, $[20..30]$ $\minute$.
\item Mix frosting, spread on top before serving.
\end{preparation}


\recipeend%
