\section[Egg Bites]{Egg Bites}\index{egg!Egg~Bites}


\begin{recipestats}[
	servings=12 jars,
	preptime=25 \minute,
	bakingtime=1 \hour,
	inactivetime=1 \hour,
	source=Mike \& Jane,
	original=\citetitle{anovaEggBites}~\cite{anovaEggBites},
	]
\end{recipestats}


\begin{recipeabstract}
	These are perfect for a quick and portable breakfast.
	Jane and I got a sous vide machine for our wedding and tried them as the inaugural recipe since they cook quickly.
	That and Jane's appreciation for Starbucks Egg Bites.
	As it turns out there are many egg bite clones available for all tastes.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[12][large]{eggs}\\
		\ingredient[1][C]{Asiago}\\
		\ingredient[8][\ounce]{mushrooms}\\
		\ingredient[6][slices]{bacon}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onehalf][C]{cream cheese}\\
		\ingredient[\approx3][\Tablespoon]{butter}\\
		\ingredient[\onefourth][tsp]{salt}\\
		\ingredient[12][4~\fluidounce]{canning jars}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Greasing the jars is important as the eggs can get stuck.}
\begin{preparation}
\item Set the water bath for $172$ \Fahrenheit~/ $77.8$ \Celsius.

\item Grease jar interiors w/ butter $\|$ crisco etc.

\item Slice mushrooms and begin to saut\`{e} w/ dash of salt. Meanwhile slice bacon in half and add.
	Remove bacon when still slightly chewy, remove mushrooms when well browned.

\item Meanwhile, grate the cheese.

\item Add bacon \& mushrooms to each jar.

\item Whisk eggs, cheeses, salt. Add egg mixture to each jar.

\item Optionally, add a small pat of butter on top to each jar.

\item Add lids to each jar and screw on lightly using only your fingertips. The goal is to allow air to release in order to prevent the jars from shattering in the bath.

\item Add jars to water bath and cook for $1\; hour$. Remove, cool, tighten lids, then refrigerate up to $\approx1 week$.

\item Reheat by:
\begin{inparaenum}[\itshape a)\upshape]
	\item microwave for $[1..1.5]$ \minute, or
	\item invert \& remove, broil for a few minutes.
\end{inparaenum}

\end{preparation}


\begin{variation}
\item Jane likes red pepper, the original recipe was bacon \& $1 C$ Gruyere.
\item Many ingredients are available, try spinach / feta, basil, chilis, chorizo, potato, tomatoes, etc.
\end{variation}


\begin{experiments}
\item The cream effects the texture of the eggs: milk produces a smooth consistency, cream is fluffier, cream \& cottage cheese ($50/50$) or cream cheese for in-between.
\end{experiments}


\recipeend%
