\section[Sauasage Casserole]{Sausage \& Mushroom Breakfast Casserole}\label{sausage_casserole_christmas}\index{egg!Sausage~Casserole}\index{Christmas!Sausage~Casserole}


\begin{recipestats}[
	servings=8,
	preptime=1 \hour,
	bakingtime=1 \hour,
	inactivetime=12 \hour,
	source=Mike \& Jane,
	original=Pam Teresi \& Southern Living '86,
]
\end{recipestats}


\begin{recipeabstract}
	A Teresi Christmas tradition.
	Prepare the night before for an easy breakfast.
	See~\ref{french_toast_casserole_christmas}~\nameref{french_toast_casserole_christmas} for the sweet counterpart.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[3][C]{croutons}\\
		\ingredient[1][\pound]{breakfast sausage}\\
		\ingredient[\onehalf][\pound]{bacon}\\
		\ingredient[4][large]{eggs}
	\end{ingredientblock}

	\begin{ingredientblock}
		\ingredient[2 \onefourth][C]{whole milk}\\
		\ingredient[16][\ounce]{mushrooms}\\
		\ingredient[2][C]{cheddar}\\
		\ingredient[\threefourth][\teaspoon]{dry mustard}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Break up sausage gradually. Be careful not to burn it.}


\begin{preparation}
\item Clean the mushrooms and slice $\approx\onefourth$ $\inch$ thick.
	Cook on medium high in a large skillet.

\item Slice bacon to $\approx2$ $\inch$ strips, add to mushrooms.

\item Begin cooking sausage on medium high in another skillet.

\item Remove bacon just before it starts to get crispy.
	Cook mushrooms and sausage until well browned.
	Set aside.

\item Grease a $13\times9''$ pan, add croutons.

\item Beat eggs in a large bowl, beat in milk, mustard.

\item Add mushrooms, bacon, sausage over croutons.
	Pour eggs over.

\item Seal with lid and refridgerate overnight.

\item In the morning, preheat oven to 350 $\Fahrenheit$.
	Remove from fridge and let stand for 30 $\minute$.

\item Bake for 50 $\minute$.
	Meanwhile, shred the cheese, set aside.

\ragmarpar{Always serve with hot sauce.}
\item Remove from oven, add cheese on top, bake another 5 $\minute$.
\end{preparation}


\begin{variation}
\item Substitute a $10.75$ $\ounce$ can of cream of mushroom soup for the mushrooms.
	Add to egg / milk mix.
\end{variation}


\recipeend%
