\section{Banana Pancakes}\index{banana!Banana Pancake}


\begin{recipestats}[
	servings=12 pancakes,
	preptime=10 \minute,
	source=Mike \& Jane,
]
\end{recipestats}

\ragmarpar{Keep your ripe bananas in the freezer and defrost prior.}
\begin{recipeabstract}
	A breakfast to make on the weekend after sleeping in.
	Save extra pancakes in foil on a single layer to bake later.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][C]{flour, all purpose}\\
		\ingredient[2][\Tablespoon]{sugar}\\
		\ingredient[2][\teaspoon]{baking powder}\\
		\ingredient[\onehalf][\teaspoon]{salt}
	\end{ingredientblock}

	\begin{ingredientblock}
		\ingredient[\onehalf][C]{greek yogurt}\\
		\ingredient[\onehalf][C]{milk, whole}\\
		\ingredient[\approx7..9][\ounce]{banana, ripe}\\
		\ingredient[1]{egg}\\
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Weigh the bananas w/ their peels.}


\begin{preparation}
	\item Sift flour, sugar, baking powder, salt, set aside.

	\item Add banana, yogurt, egg, milk to a small bowl.
		Mix on low with a hand mixer until mostly smooth.

	\item Fold in the flour to the banana mixture until just combined.

	\ragmarpar{An iron skillet is critical; preheat on medium low.}
	\item Add a small amount of butter or oil to your skillet, then two spoonfulls of batter per each cake.
		Cook on first side until bubbles come through.
		Flip and cook until lightly brown, $\approx2$ \minute.

	\item Adjust heat after each batch if necessary, repeat.

	\item Serve w/ syrup and apricot or strawberry jam.
\end{preparation}


\begin{experiments}
	\item Try adding some vanilla extract.

	\item Try replacing a little powder with soda.
\end{experiments}


\recipeend%
