\section[Egg Bites]{Egg Bites}
\index{egg!Egg~Bites}


\begin{recipestats}[
	servings=12 jars,
	preptime=15 \minute,
	bakingtime=1 \hour,
	source=Anova Culinary,
	]
\end{recipestats}


\begin{recipeabstract}
	These are perfect for a quick and portable breakfast.
	Jane and I got a sous vide machine for our wedding and tried them as the inaugural recipe since they cook quickly.
	That and Jane's appreciation for Starbucks Egg Bites.
	As it turns out there are many egg bite clones available and we felt this was a classic flavor combination.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
	\ingredient[12][large]{eggs}\\
	\ingredient[1][C]{Gruyere}\\
	\ingredient[\nicefrac{1}{2}][C]{cream cheese}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onefourth][tsp]{salt}\\
		\ingredient[6][slices]{bacon}\\
		\ingredient[12][4~\fluidounce]{canning jars}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{greasing the jars is important as the eggs can get stuck}
\begin{preparation}
\item Set the water bath for $172$ \Fahrenheit / $77.8$ \Celsius.

\item Grease jar interiors w/ butter $\|$ crisco etc.

\item Cook bacon \& cut slices in half. Grate cheese.

\item Add half of a bacon slice to each jar.

\item Blend eggs, cheeses, salt. Add egg mixture to each jar.

\item Add lids to each jar and screw on lightly using only your fingertips. The goal is to allow air to release in order to prevent the jars from shattering in the bath.

\item Add jars to water bath and cook for $1\; hour$. Remove, cool, tighten lids, and refrigerate up to $\approx1 week$.

\item Reheat by:
\begin{inparaenum}[\itshape a)\upshape]
	\item microwave for $[1...1.5]$ \minute, or
	\item invert \& remove, broil for a few minutes.
\end{inparaenum}

\end{preparation}


\begin{variation}
	\item Jane likes red pepper, I like Asiago $\&$ mushroom.
	\item The cream effects the texture of the eggs: milk produces a smooth consistency, cream is fluffier, cream \& cottage cheese ($50/50$) or cream cheese for in-between (needs more experimentation).
\end{variation}


\begin{experiments}
\item This recipe may need some more salt, other resources recommend a ratio of $300g$ eggs (about 6), $300g$ cream, $3g$ salt, but omit the cheese.
\item This recipe might benefit from butter / olive oil beaten into the eggs.
\end{experiments}


\recipeend
