\section[Carnitas]{Carnitas, or Little Meats}\index{pork!Carnitas}\index{orange!Carnitas}


\begin{recipestats}[
    servings=8,
    preptime=45~\minute,
    bakingtime=5~\hour,
    source=Mike \& Jane,
    original=Rick~\cite{baylessCarnitas} \& Rick~\cite{martinezCarnitas},
]
\end{recipestats}


\ragmarpar{Mexican oregano is best.}
\begin{recipeabstract}
    Pork shoulder confit.
    Bayless provides methods to recreate the dish in lieu of a giant copper cauldron full of lard.
    The slow cooker method is adapted here, which allows for some spice as frying in lard would otherwise `obliterate' it.
    Spices are usually either just salt \& pepper, or cinnamon, citrus, oregano, etc.
    Martinez recommends Ceylon (canela) which has a sweeter flavor than cassia.
    People often include ingredients to encourage browning such as cola, citrus, condensed milk, or sugar.
\end{recipeabstract}
\ragmarpar{The Ricks recommend Pico de Gallo or Guacamole.}


\begin{ingredientcolumns}
    \begin{ingredientblock}
        \ingredient[4][\pound]{pork butt}\\
        \ingredient[1][\Tablespoon]{salt}\\
        \ingredient[4][\ounce]{lard}\\
        \ingredient[12][\fluidounce]{Negra Modelo}\\
        \ingredient[1][C]{stock}\\
        \ingredient[2][\Tablespoon]{brown sugar}\\
        \ingredient[\onehalf][]{white onion}\\
        \ingredient[1][\ensuremath{{ft}^2}]{cheesecloth}
    \end{ingredientblock}
    \begin{ingredientblock}
        \ingredient[2][]{oranges}\\
        \ingredient[2][]{limes}\\
        \ingredient[2][\teaspoon]{oregano}\\
        \ingredient[2][\teaspoon]{peppercorns}\\
        \ingredient[2][\teaspoon]{chili flakes}\\
        \ingredient[1][head]{garlic}\\
        \ingredient[2][leaf]{bay}\\
        \ingredient[2][stick]{canela}
    \end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{Lightly crack the pepper}


\begin{preparation}
\item Reserve a large dutch oven \& iron skillet, preheat to $250$ $\Fahrenheit$.
\item Melt sugar in the stock.
\item Debone pork butt, cut into large chunks, salt, set aside.
    \ragmarpar{Dice remaining onion for tacos.}
\item Melt lard on medium, add pork, stock, beer.
\item Cut garlic head in half, add to cheesecloth with oregano, peppercorns, chili flakes.
\item Cut the onion and citrus in half.
\item Add cinnamon, bay leaf, onion; submerge the sachet.
    \ragmarpar{Stir occasionally.}
\item Squeeze the citrus, add juice and one orange peel.
\item Bring to a low simmer.
\item Roast covered $\approx3$ $\hour$, or until it reaches 203 $\Fahrenheit$.
\item Lower to $200$ $\Fahrenheit$, uncover, roast $2$ $\hour$.
    \ragmarpar{Strain braising liquid, save fat for tortillas.}
\item Remove from oven, remove peel, sachet, canela, bay leaf.
\item Transfer pieces to a cutting board, chop.
\item Broil or fry the pork in the skillet w/ liquid to brown.
\item Serve with lime wedges, cotija, diced white onion.
\end{preparation}


\recipeend%
