\section[Cornish Hens]{BBQ Cornish Hens}\index{BBQ!Cornish~Hens}\index{chicken!Cornish~Hens}


\begin{recipestats}[
	servings=$\approx$~24,
	preptime=1~\hour,
	bakingtime=$\approx$3~\hour,
	source=Kevin \& Mike,
]
\end{recipestats}

\ragmarpar{$\approx [\onehalf .. 1]$  Cornish Hen per person.}
\begin{recipeabstract}
	A big batch of barbeque chicken.
	Cook time is reduced by butterflying the poultry, and using cornish hens over chicken.
\end{recipeabstract}


\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[16][]{Cornish Hens}\\
		\ingredient[2][C]{\reffull{double_duece_rub}}\\
		\ingredient[\approx~4][\pound]{charcoal}\\
		\ingredient[\approx~2][\pound]{hickory}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Thick white smoke tastes bad! It's creosote.}
\begin{preparation}
\item Prepare rub ahead of time, leaving pepper / chile rubs separate.
\item Spatchcock the poultry.
	Cut out the spine with shears and flatten it.
	Be \textit{extremely} cautious with the scissors and do not cut your fingers!
\item Season chicken w/ pepper rub then chile, using an even amount.
\ragmarpar{Dissipate white smoke by adding air or heat.}
\item Bring grill to $250$ \Fahrenheit, add an aluminum can of water.
\item Add your choice of hardwood and let it light.
\item Add to poultry to grill.
\item Add fuel \& rotate poultry every $[20 .. 30]$ \minute.
	Maintain $[225 .. 250]~\Fahrenheit$.
\item Start probing the poultry about 2 \hour~in.
	Aim for $155$ \Fahrenheit and rotate / flip as necessary.
\ragmarpar{Wood burns hotter than charcoal; it's easier to manage.}
\item Serve whole or divide the breast / leg quarter.
\end{preparation}


\recipeend%
