\section{Smoked Turkey}


\begin{recipestats}[
	servings=1\onefourth~\pound/person,
	preptime=45~\minute,
	bakingtime=$\approx5~\hour$,
	inactivetime=30~\minute,
	source=Teresi~Family,
]
\end{recipestats}


\begin{recipeabstract}
	A Teresi family tradition.
	Moving the turkey or ham to the grill frees up the oven for other dishes.
	Use the resting time as a buffer to help you reach your desired time to serve the meal.
\end{recipeabstract}


\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[1][]{turkey}\\
		\ingredient[\approx4][\pound]{charcoal}\\
		\ingredient[\approx1][\pound]{hardwood}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\ragmarpar{Use the Tip Top Temp to maintain the grill.}
\item Thaw the turkey in fridge at $\approx40$ $\Fahrenheit$, for 24 $\hour$ per $4~\pound$ of turkey.
	Cook turkey within 4 $day$ after thawing.
\item Prepare a rub the night or morning before.\\
	Remove and save neck and etc for making gravy.
\item Calculate time to start cooking given your target serving time.
	Afford $\approx30$ $\minute$ to light the grill and also to rest.
	See chart below.
\ragmarpar{Hickory and pecan is best.}
\item Fill a chimney $\approx$ $\onethird$ full, light.
	Scrape the grate.
	Add an aluminum pan to the middle of the bottom grate.
\item Split coal to both sides, add top grate, let heat for a few minutes and clean the grate with a wet paper towel.
	Add probe to grill grate.
\item Bring to 275 \Fahrenheit.
	Move turkey to center, add a probe to the turkey.
\ragmarpar{If you have white smoke you need more heat!}
\item Add hardwood to smoke for the first $\approx2$ $\hour$.
\item Maintain $[250..275]$ checking every $\approx20$ $\minute$ to add coal.
\item Remove turkey when it reaches 160 $\Fahrenheit$, move to a pan and cover with foil. Let rest 30 $\minute$.
\end{preparation}


\begin{center}
	\begin{tabular}{ll}\toprule
		\textbf{temperature}  &  \textbf{cooking rate} \\ \midrule
		225~\Fahrenheit       &  30~\minute/\pound\\
		250~\Fahrenheit       &  25~\minute/\pound\\
		275~\Fahrenheit       &  20~\minute/\pound\\ \bottomrule
	\end{tabular}
\end{center}


\recipeend%
