\section[Steak Fajitas]{Skirt Steak Fajitas}\index{beef!Steak~Fajitas}


\begin{recipestats}[
	servings=4,
	preptime=30~\minute,
	bakingtime=15~\minute,
	inactivetime=4~\hour,
	source=Mike \& Jane,
]
\end{recipestats}


\begin{recipeabstract}
	A quick and easy steak fajita.
	The steak is also great on salads.
	Watch the grill as it cooks quickly.
\end{recipeabstract}


\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[24][\ounce]{skirt steak}\\
		\ingredient[][]{\reffull{fajita_no_4}}\\
		\ingredient[16][small]{tortilla}\\
		\ingredient[2][]{poblano or cubanelle}\\
		\ingredient[1][]{onion, white}\\
		\ingredient[1][C]{cotija}\\
		\ingredient[][]{sour cream}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Sliced peppers last $\approx 3$ $days$ in the fridge.}
\begin{preparation}
\ragmarpar{Use less rub than for chicken, but be generous.}
\item Prepare the rub ahead of time.
\item Prepare the toppings ahead of time, refrigerate.
	Dice white onion, cotija.
	Wash and slice poblano into $\approx 1$ $cm$ strips.
\item Add the rub to the steak with a little oil, pierce w/ fork.
\item Marinade $\approx 4$ $\hour$ or overnight.
\item Heat grill to $\approx 350$ $\Fahrenheit$, clean the grate, add wood.
\item Add steak to grill off the heat for $\approx 10$ $\minute$.
\ragmarpar{Cherry or pecan wood is best.}
\item Meanwhile saut\'{e} the peppers on high until blistered.
\item Meanwhile, preheat oven to 250 $\Fahrenheit$.
\item Take steak off once it reaches $\approx [120 .. 130]$ $\Fahrenheit$.
	Rest $[5..10]$ $\minute$.
\item Meanwhile warm up some tortillas in the oven or an iron skillet.
\ragmarpar{Keep the toppings simple}
\item Slice the steak across the grain $\approx 2$ $mm$ thick.
	Add a dash of the rub and say ``Bam!''.
\end{preparation}


\recipeend%
