\section[Mai Tai]{Mai Tai\ragStars{3}}
\index{rum!Mai Tai}
\index{orgeat!Mai Tai}

\begin{recipestats}[
	servings=1,
	preptime=5 \minute,
	original=\citefield{cocktailSeminars2021}{title} \cite{cocktailSeminars2021},
]
\end{recipestats}


\begin{recipeabstract}
	``Maita'i roe a'e!'', or, ``Out of this world!''.
	A famous tiki drink known for its nebulous origin and use of multiple rums, claimed by both Trader Vic and Don the Beachcomber.
	The prevailing recipe of today appears to hail from Trader Vic who resorted to blending rum when his preferred 17-year-old Wray \& Nephew was no longer available.
	The short of it is that variations abound and you should feel free to experiment.

\end{recipeabstract}


\ragmarpar{Imagine the lime shell \& mint is a small deserted island.}
\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[2][\fluidounce]{rum, aged}\\
		\ingredient[\threefourth][\fluidounce]{lime juice}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[\onehalf][\fluidounce]{cura\c{c}ao}\\
		\ingredient[\onehalf][\fluidounce]{orgeat}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Add to shaker, fill with crushed ice, shake.
\item Pour all contents into double old fashioned.
\item Garnish with a sprig of mint and the peel of half of a spent lime.
\end{preparation}


\begin{variation}
\item One common variation is to sub the aged rum with 1 $\onehalf$ $\fluidounce$ white and $\onehalf$ $\fluidounce$ dark rum.
\item Floating the dark rum on top after the shake/pour is also common.
\end{variation}


\recipeend
