\section[Super Joose]{Super Joose, or,\\Acid Adjusted Citrus}


\begin{recipestats}[
	servings=$\approx 12$ \fluidounce,
	preptime=30 \minute,
	inactivetime=2 \hour,
	original=\citeauthor{superJuiceKos} \cite{superJuiceKos},
]
\end{recipestats}


\ragmarpar{Use a sharp peeler to minimize the pith cut from the peel.}
\begin{recipeabstract}
	A shelf stable and high yielding preparation for citrus juice.
	Peels are combined with acids, diluted, blended, and strained.
	The recipe addresses two issues: succinic acid causes oxidation, and the peels are normally wasted.
	The solution is to use an oleo citrate by dissolving the citrus oil with citric and malic acids, then combine it with the original juice.
	The overall reduction in succinic acid results in a longer shelf life and the incorporation of the peel produces a higher yield.
	Oleo citrate is very similar to oleo saccharum which uses sugar instead of acid, commonly used for punch\cite{oleoSaccharum}.
\end{recipeabstract}


\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[2][]{limes}\\
		\ingredient[\twothird][x\;weight \; of \; peel]{citric acid}\\
		\ingredient[\onethird][x\;weight \; of \; peel]{malic acid}\\
		\ingredient[16 \; \twothird][x\;weight \; of \; peel]{water}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
	\ragmarpar{Rinse out jar w/ part of the water to get it all into the blender.}
\item Peel the citrus and measure the weight of the peels.
\item Measure the acids by weight compared to the weight of the peels.
\item Combine acids and peels in a jar, shake, and macerate $[1 .. 2]$ $\hour$.
\item Juice the fruit, combine everything (w/ peels), blend for 2 \minute.
\item Strain w/ cheescloth, squeeze to get all the juice out.
\item Bottle and refrigerate up to 2 \week.
\end{preparation}


\begin{variation}
	\ragmarpar{\citeauthor{superJuiceKosGrapefruitYT} advises super grapefruit may not be a good 1:1 sub for squeezed since the peels are strongly flavored\cite{superJuiceKosGrapefruitYT}.}
\item Other citrus varieties are available using the following ratios\cite{superJuiceKosGrapefruit}\cite{superJuiceKos}.
	Note that grapefruit is the only one using \acrshort{MSG}, which is used as a substitute for glutamic amino acid\cite{superJuiceKosGrapefruitYT}.
	\begin{center}
		\begin{tabular}{lSSSS}\toprule
			\textbf{ingredient}     &  \textbf{lime} & \textbf{lemon} & \textbf{orange} & \textbf{grapefruit} \\ \midrule
			\textit{citric acid}    &           0.66 &           1.00 &            0.90 &                0.80 \\
			\textit{malic acid}     &           0.33 &                &            0.10 &                0.20 \\
			\textit{water}          &          16.66 &          16.66 &           16.66 &               16.66 \\
			\textit{\acrshort{MSG}} &                &                &                 &               0.033 \\ \bottomrule
	\end{tabular}
	\end{center}
\end{variation}


\recipeend
