\section{Eggplant Lasagna}

\begin{recipestats}[
	servings=8 servings,
	preptime=75 minutes,
	bakingtime=60 minutes,
	source=The Teresi Family,
]
\end{recipestats}

\ragmarpar{Also take a look at \citetitle{cakeBoss2012} \cite{cakeBoss2012} for a bit of technique}
\begin{recipeabstract}
	We like to make this on the weekends for quick meals later on.
	There is a lot of leeway so feel free to experiment.
	This features hot Italian sausage, eggplant, and plenty of basil.
\end{recipeabstract}

\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][bottle]{Chianti}\\
		\ingredient[1][lb]{italian sausage}\\
		\ingredient[1][lb]{eggplant}\\
		\ingredient[1][large]{onion, white}\\
		\ingredient[28][\ounce]{tomatoes}\\
		\ingredient[15][\ounce]{tomato sauce}\\
		\ingredient[6][\ounce]{tomato paste}\\
		\ingredient[6][cloves]{garlic}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[12][\ounce]{mozarrella}\\
		\ingredient[15][\ounce]{ricotta}\\
		\ingredient[4][\ounce]{parmasan}\\
		\ingredient[\approx \threefourth][lb]{lasagna noodles}\\
		\ingredient[\approx 2][\Tablespoon]{basil, fresh}\\
		\ingredient[\onehalf][\Tablespoon]{italian seasoning}\\
		\ingredient[\approx \onefourth][\teaspoon]{chili flakes}\\
		\ingredient[\approx \onefourth][\teaspoon]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}

\ragmarpar{hot italian sausage is best; also consider a thin skinned eggplant}

\begin{preparation}
\item Open the Chianti and queue some Luciano Pavarotti.
\item Heat $\approx 1$ \Tablespoon~oil in a frying pan on medium high.
	Meanwhile chop the onions.
	Toss into pan with some salt and reduce to medium low, stirring occasionally.
\item Meanwhile prep the vegetables.
	Dice the eggplant into $\approx\onehalf$ $inch$ cubes, toss w/ dash of salt.
	Pick the basil and rinse.
	Smash and peel the garlic.
	Dice the tomatoes.
\item Begin cooking the sausage.
	Brown the sausage on medium high in large saut\`{e} pan, breaking it apart as you go.
	Deglaze occasionally with a splash of Chianti.
\ragmarpar{saut\`{e}ing the tomato paste sweetens the sauce by caramlizng the sugars}
\item When the sausage is browned enough, reduce to medium, transfer onions to sausage.
	Begin cooking eggplant in the frying pan in batches, stirring periodically.
	Crush garlic into the sausage, add italian seasoning \& chili flakes, mix and cook $[1 \dots 2]$ $min$.
	Stir in tomato paste and cook for $\approx 2$ $min$.
	Deglaze the sausage with the Chiant to break up the fond.
\item Add tomatoes, tomato sauce, \onehalf~minced basil.
	Bring to a boil, then reduce and let simmer for $\geq 15$ $min$.
	Periodically check on the eggplant and transfer when browned enough.
\ragmarpar{the sauce can be made ahead of time as well}
\ragmarpar{pre-cooked noodles work well}
\item Begin cooking lasagna noodles if necessary, drain and set aside.
	Preheat oven to $375$ \Fahrenheit.
\item Meanwhile, shread mozarella and parmasan.
	Mix ricotta, remaining basil minced, egg, \onehalf~parmasan in a large bowl.
\item Assemble the layers into a $\approx 13~x~9.5~x~2.5"$ ($\approx 2$ $quart$) baking dish.
	You will need to roughly divide the sauce into fourths, and everything else into thirds.
	First add a layer of sauce, then noodles.
	Then in this order: ricotta, mozarella, sauce, noodles.
	Repeat once more for a total of 3 noodle layers.
	Top with sauce, then remaining parmasan.
\item Cover dish with foil, bake $40$ $min$, uncover and bake $10$ $min$, remove and rest $\approx 10$ $min$.
	Top with olive oil.
\end{preparation}

\begin{variation}
	\item Try adding minced sun dried tomatoes and / or mushrooms.
	\item See the parent recipe in \citetitle{newCookBook2014} \cite{newCookBook2014} for list of substitutions such as using bacon / pancetta, cream cheese in place of ricotta, etc.
\end{variation}

\recipeend
