\section{Fettuccine Alfredo}
\index{pasta!Fettucine Alfredo}


\begin{recipestats}[
	servings=2 people,
	preptime=15 \minute,
	bakingtime=20 \minute,
	source=Mike \& Jane,
	original=\citetitle{newCookBook2014} \cite{newCookBook2014},
	]
\end{recipestats}

\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[8][\ounce]{fettuccine, dry}\\
		\ingredient[4][\ounce]{mushrooms}\\
		\ingredient[2][\ounce]{Asiago}\\
		\ingredient[\approx 4][cloves]{garlic}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[3][\Tablespoon]{butter, unsalted}\\
		\ingredient[1][C]{cream, heavy}\\
		\ingredient[\onehalf][\teaspoon]{salt}\\
		\ingredient[\oneeighth][\teaspoon]{pepper}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\ragmarpar{Stir mushrooms occasionally, cook to well done.}
\item Slice mushrooms, begin to saut\`{e} on medium w/ dash of oil.

\item Cook pasta in salted water to al dente, then toss with oil.
	Meanwhile grate chese, crush garlic.

\item Saut\`{e} crushed garlic in butter in a large saucepan $\approx1$ \minute~on medium-high.

\ragmarpar{Use a bit of the pasta water to thicken the sauce.}
\item Add cream, salt, pepper to sauce. Bring to boil then reduce heat, simmer uncovered $\approx3$ \minute or until it begins to thicken.

\item Remove from heat add cheese \& mushrooms.

\item Add pasta to sauce, toss to combine.
\end{preparation}


\begin{variation}
\ragmarpar{Pecorino Romano does not melt well for use in the sauce.}
\item Try Parmesan instead of Asiago, mushrooms are optional.

\item For shrimp alfredo add $\approx8\; \ounce$ prior to removing from heat, cook through and continue.
\end{variation}


\recipeend
