\section[Lasagna]{American Lasagna}
\index{pasta!American~Lasagna}
\index{sausage!American~Lasagna}


\begin{recipestats}[
	servings=12 servings,
	preptime=1\onehalf~ \hour,
	bakingtime=1~ \hour,
	source=Teresi Family,
]
\end{recipestats}


\ragmarpar{See \citetitle{cakeBoss2012} \cite{cakeBoss2012} for technique}
\begin{recipeabstract}
	We like to make this on the weekends for quick meals later on.
	There is a lot of leeway so feel free to experiment.
	This features hot Italian sausage, eggplant, and plenty of basil.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][bottle]{Chianti}\\
		\ingredient[1][lb]{italian sausage}\\
		\ingredient[1][lb]{eggplant}\\
		\ingredient[1][large]{onion, white}\\
		\ingredient[28][\ounce]{tomatoes}\\
		\ingredient[15][\ounce]{tomato sauce}\\
		\ingredient[2][\Tablespoon]{tomato paste}\\
		\ingredient[6][cloves]{garlic}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[12][\ounce]{mozarrella}\\
		\ingredient[15][\ounce]{ricotta}\\
		\ingredient[4][\ounce]{parmasan}\\
		\ingredient[\approx \threefourth][lb]{lasagna noodles}\\
		\ingredient[\approx 2][\Tablespoon]{basil, fresh}\\
		\ingredient[\onehalf][\Tablespoon]{italian seasoning}\\
		\ingredient[\approx \onefourth][\teaspoon]{chili flakes}\\
		\ingredient[\approx \onefourth][\teaspoon]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}
\ragmarpar{use hot italian sausage, 28 \ounce~either canned or fresh tomatoes}


\begin{preparation}
\item Open the Chianti and queue some Luciano Pavarotti.
	Reserve a large saut\`{e} pan, frying pan, and a $\approx 9\; x\; 13"$ baking dish.

\item Begin saut\`{e}ing onions in frying pan.
	Heat $\approx 1$ $\Tablespoon$ oil, medium high.
	Quarter onions, then slice along the axis.
	Add to pan w/ dash of salt, reduce to medium, stir occasionally.

\item Preheat oven to $375$ \Fahrenheit.
	If using dry raw noodles, begin that recipe according to your package directions.

\item Meanwhile prep the vegetables.
	Dice the eggplant into $\approx \onehalf "$ cubes, toss w/ dash of salt.
	Pick the basil and rinse.
	Smash and peel the garlic.
	Dice the tomatoes.
	Measure the dry spices.

\item Shred or slice ($\approx \oneeighth "$) the mozarella.
	Shred the parmasan.

\ragmarpar{saut\`{e}ing the tomato paste sweetens the sauce by caramlizng the sugars}
\item Brown the sausage on medium high in large saut\`{e} pan, while breaking it apart.
	Deglaze w/ some Chianti.

\item When the sausage is browned enough, reduce to medium, transfer onions to sausage.
	Begin cooking eggplant in the frying pan in batches on medium low, stirring periodically.

\item Crush garlic into the sausage, add italian seasoning \& chili flakes, mix and cook $\approx 2$ \minute.
	Stir in tomato paste and cook for $\approx 2$ \minute.
	Deglaze w/ the Chianti to break up the fond.

\item Add tomatoes, tomato sauce, minced basil.
	Bring to a boil, then reduce and let simmer for $\geq 15$ \minute.
	Periodically check on the eggplant and transfer when browned enough.

\item Mix ricotta, egg, \onehalf~parmasan in a large bowl.

\item Taste the sauce and season accordingly.

\item Assemble the layers into baking dish.
	You will need 4 layers of sauce, 3 noodles, and 2 ricotta.
	First add a layer of sauce, then noodles.
	Then in order: ricotta, sauce, mozarella, noodles.
	Repeat.
	Top w/ sauce, then remaining parmasan.

\item If necessary, cover with foil according to the pasta instructions.
	Bake 50 \minute, rest 10 \minute.
\end{preparation}


\begin{variation}
\item Try adding minced sun dried tomatoes and/or mushrooms.

\item See \citetitle{newCookBook2014} \cite{newCookBook2014} for substitutions such as bacon / pancetta, cream cheese in place of ricotta, etc.

\item One can make the sauce ahead of time, and/or assemble and freeze before baking.
\end{variation}


\recipeend
