\section[Beef Bowl]{Mexican Beef Bowl}\label{mexican_beef_bowl}\index{chili!Beef Bowl}\index{beef!Beef Bowl}


\begin{recipestats}[
	servings=4 people,
	preptime=30 \minute,
	bakingtime=30 \minute,
	source=Mike \& Jane,
	original=\citeauthor{blueApronBeefBowl}~\cite{blueApronBeefBowl}
	]
\end{recipestats}


\begin{recipeabstract}
	Full flavored and complex.
	This recipe introduced us to the chili baked carrots which are excellent on their own.
	The tomatoes, sauce, and cotija balance out the spicy beef.
\end{recipeabstract}


\ragmarpar{Add a chile de \'{a}rbol to taste (or cayenne).}
\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][lb]{ground beef}\\
		\ingredient[\onehalf][lb]{tomatoes, cherry}\\
		\ingredient[\onehalf][lb]{carrots}\\
		\ingredient[1]{lime}\\
		\ingredient[\onefourth][C]{jalepe\~{n}os, pickled}\\
		\ingredient[\onefourth][C]{mayonnaise}\\
		\ingredient[\approx~8][oz.]{cheese, cotija}\\
		\ingredient[\approx~1][C]{rice}\\
		\ingredient[\approx~3][\Tablespoon]{spice blend}
	\end{ingredientblock}
	\begin{ingredientblock}[spice blend]
		\ingredient[2][\Tablespoon]{guajillo}\\
		\ingredient[1][\Tablespoon]{ancho}\\
		\ingredient[1][\Tablespoon]{paprika, smoked}\\
		\ingredient[1][\Tablespoon]{cumin}\\
		\ingredient[1][\Tablespoon]{marjoram}\\
		\ingredient[\onehalf][\Tablespoon]{garlic powder}\\
		\ingredient[\onehalf][\Tablespoon]{salt}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{For dried chilis: remove seeds, toast $\approx3$ \minute~\@ $350$ \Fahrenheit, grind.}

\begin{preparation}
\item Prepare ground spice blend; ahead of time if preferred.

\item Begin to brown the beef in large saut\'{e} pan, stirring occasionally. Reach a strong color at end of recipe.

\item Dice carrots, toss with oil and spices. Preheat oven to $450$ \Fahrenheit.

\item Begin cooking rice.

\item Roast carrots in oven on a cookie sheet, $[12..14)$ \minute.

\item Dice tomatoes, finely dice jalepe\~{n}os, combine with juice of 1/2 of lime, pickled jalepe\~{n}o juice to taste.

\item Add spices to beef ($\approx~3/4\ \Tablespoon$) at end, cook $\approx1~\minute$.\\
	Add $\onefourth\;C$ water, cook $[2..3)$ \minute.

\item Combine mayonnaise and juice of 1/2 lime.\\Add pickled jalepe\~{n}o juice to taste.

\item Serve by layering rice, beef, vegetables, pickled jalepe\~{n}os, cheese, mayonnaise.
\end{preparation}

\ragmarpar{We particularly appreciate the cauliflower rice version.}
\begin{variation}
\item Substitute riced cauliflower in place of rice. Cut into small pieces, chop in food processor with garlic, optionally pan fry.
\item Substitute Chorizo in place of beef, reduce spices.
\item Cotija cheese is worth the effort to find it, but mozzarella works.
\item For convenience, regular pre-ground chili powder can replace the guajillo. Similarly ancho powder is readily available.
\end{variation}

\recipeend%
