\section[Tacos Al Pastor]{Tacos Al Pastor~\vegan}\index{pork!Pork~Al~Pastor}


\begin{recipestats}[
	servings=8 people,
	preptime=2 \hour,
	bakingtime=8 \hour,
	inactivetime=$[3 \ldots 12]~\hour$,
	source=Mike \& Jane,
	original=\citeauthor{rMartinezTacos2015}~\cite{rMartinezTacos2015},
]
\end{recipestats}


\begin{recipeabstract}
	Shepherd's style tacos features a mix of Mexican \& Lebanese spices.
	It is traditionally cooked on a vertical spit and the exterior is thinly sliced through the day.
	Here we use a barbeque in lieu of a motorized trompo, which although not traditional, is more available.
\end{recipeabstract}

\ragmarpar{See~\cite{rMartinezTacos2015} for a inspiration and a pineapple salsa.}
\begin{ingredientcolumns}[1]
	\begin{ingredientblock}
		\ingredient[3][\pound]{pork shoulder}\\
		\ingredient[][]{\reffull{marinade_al_pastor}}\\
		\ingredient[10][\ounce]{pineapple, sliced}\\
		\ingredient[32][6~\inch]{tortillas}\\
		\ingredient[2]{lime}\\
		\ingredient[2][C]{cabbage}\\
		\ingredient[1]{onion, white}\\
		\ingredient[4][\ounce]{cotija cheese}\\
		\ingredient[][]{\reffull{pickled_red_onions}}\\
		\ingredient[][]{\reffull{pickled_radishes}}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{Half of a 20 $\ounce$ can of pineapple is perfect.}
\begin{preparation}
\item Prepare quick pickled vegetables $\ge 1$ \week~in advance if desired.

\item Prepare marinade.
	Reserve $\approx 1 \dots 2$ $C$ for serving later.

\item Slice pork $\approx \onehalf~\inch$, flatten with a mallet.
	Marinade $3 \dots 12~\hour$.

\item Light barbeque to your preferred temperature ($\approx 225 \dots 250~\Fahrenheit$).

\item Meanwhile layer the pork on the vertical skewer.

\ragmarpar{In lieu of a skewer you might barbeque whole or grill the slices.}
\item Barbeque $\approx 2~\hour / \pound$ to a target of $195~\Fahrenheit$ (minimum $145~\Fahrenheit$).
	Pull off and let rest in a cool oven $\approx 30~\min$.

\item Meanwhile prepare the toppings.
	Dice the onion, pineapple.
	Julienne the cabbage.
	Shred the cotija.
	Quarter the limes.

\item Prepare the sauce.
	Heat $\approx 2~\Tablespoon$ oil in a sauce pan.
	Add the reserved marinade, cook a few minutes, take off heat.

\item Transfer pork to a cutting board and thinly slice.

\item Heat a frying pan with a bit of oil.
	Grill tortillas $\approx 30~\second$ per side.
	Serve with pork, pineapple, and preffered toppings.
\end{preparation}


\begin{variation}
\item Traditional toppings are cilantro, diced onion, grilled pineapple.

\item Try grilling, baking, or barbequing whole in lieu of the spit.

\item Pork is traditional but chicken and fish work too.
	Try baking boneless chicken thighs.
\end{variation}


\recipeend%
