\section[Spinach Quiche]{Spinach Artichoke Quiche}
\index{egg!Spinach Quiche}
\index{quiche!Spinach}


\begin{recipestats}[
	servings=4 people,
	preptime=45 \minute,
	bakingtime=45 \minute,
	source=Mike \& Jane,
	original=\citefield{joyofcooking2006}{title} \cite{joyofcooking2006},
	]
\end{recipestats}


\begin{recipeabstract}
	A classic dish.
	We like to serve this as a side along with cardamom rice and have leftovers for breakfast.
\end{recipeabstract}
\ragmarpar{See \ref{basicFlakyPiePastry} for pastry recipe.}


\begin{ingredientcolumns}
	\begin{ingredientblock}
		\ingredient[1][]{pie pastry}\\
		\ingredient[6][large]{eggs}\\
		\ingredient[1][C]{cream}\\
		\ingredient[2\;\onehalf][C]{spinach}\\
		\ingredient[1\;\onehalf][C]{Asiago}\\
		\ingredient[6][\fluidounce]{artichokes}
	\end{ingredientblock}
	\begin{ingredientblock}
		\ingredient[1][]{onion, white}\\
		\ingredient[3][Tbs]{butter}\\
		\ingredient[2][\teaspoon]{garlic}\\
		\ingredient[\onefourth][\teaspoon]{salt}\\
		\ingredient[\onehalf][\teaspoon]{pepper, white}\\
		\ingredient[\onehalf][\teaspoon]{marjoram}
	\end{ingredientblock}
\end{ingredientcolumns}


\begin{preparation}
\item Reserve a large bowl and large pie pan.

\ragmarpar{If using pre-mad pastry, roll it out a little more.}
\item Prepare pastry and chill prior.
	Preheat oven to $400$ \Fahrenheit.

\item Measure spinach, artichokes. Grind salt, pepper, marjoram.

\item Begin to cook the onion.
	Slice onion, cook over medium-low heat with a little olive oil while stirring occasionally.

\ragmarpar{See \ref{basicFlakyPiePastry} for more partial prebake details.}
\item Begin to partially prebake the pastry.
	Butter pie pan, add pastry, pre-bake for 15 $\minute$ @ $400\;\Fahrenheit$ w/ weights, $[10..12]$  $\minute$ @ $375\;\Fahrenheit$ w/o weights.
	Set aside 1 egg yolk and immediately brush with egg yolk when removed from oven.

\item Meanwhile, roughly chop artichokes \& spinach, shred cheese.

\item Prepare vegetables.
	Add spinach to onions.
	Add garlic, butter, and cook $\approx 1$ \minute, take off the heat.

\item Combine remaining eggs, cream, salt, pepper, marjoram.

\item Layer into pie: cheese, vegetables, egg mixture.
	Optionally garnish with $\onehalf$ $\teaspoon$ paprika for some pizzazz.

\ragmarpar{Check @ 20 \minute~ and add foil to edges if needed to prevent burning.}
\item Bake at $375$ \Fahrenheit~for $30$ \minute, broil briefly, rest $10$ \minute.
\end{preparation}


\begin{variation}
\item Quiche Lorraine uses bacon and Gruyere, quiche Florentine is spinach and Gruyere, and leek and onion appear popular.

\item Other milk varieties are available but heavy cream will make the best texture in my humble opinion.
\end{variation}


\recipeend
