\section[Turkey Injection]{Turkey Injection Marinade}


\begin{recipestats}[
	servings=$[15..20]~\pound$ turkey,
	preptime=10~\minute,
	inactivetime=2~\hour,
	source=Mike \& Steve,
	original=\citefield{spruceTurkeyInjection}{shorttitle}~\cite{spruceTurkeyInjection},
]
\end{recipestats}

\begin{recipeabstract}
	Don't let that turkey dry out!
	A Teresi Thanksgiving tradition for smoking the turkey.
	Some turkeys are pre-brined so brining those may result in too much salt.
	If the label lists language such as ``injected with an 8\% solution of...'', then it is 'pre-brined' or 'self-basted'.
	This recipe however does not have a lot of salt and we've had success with a pre-brined turkey.
\end{recipeabstract}


% TODO need a 'northwoods fire' clone from Penzey's
% https://www.penzeys.com/online-catalog/northwoods-fire-seasoning/c-24/p-504/pd-s
% coarse flake salt, paprika, ground chipotle pepper, black pepper, cayenne red pepper, thyme, rosemary and granulated garlic
\pagebreak[4]
\begin{ingredientcolumns}
	\begin{ingredientblock}[marinade]
		\ingredient[\onehalf][C]{chicken broth}\\
		\ingredient[2][\Tablespoon]{butter, unsalted}\\
		\ingredient[1][\Tablespoon]{lemon juice}\\
		\ingredient[1][\teaspoon]{black pepper}\\
		\ingredient[\onehalf][\teaspoon]{garlic powder}\\
		\ingredient[\onehalf][\teaspoon]{kosher salt}
	\end{ingredientblock}

	\columnbreak
	\begin{ingredientblock}[rub]
		\ingredient[2][\Tablespoon]{butter, unsalted}\\
		\ingredient[1][\Tablespoon]{Penzey's Northwoods}
	\end{ingredientblock}
\end{ingredientcolumns}


% TODO add turkey thawing instructions, add to it's own 'recipe'?
% TODO add turkey smoke instructions
\begin{preparation}
\item Thaw the turkey; plan to inject $\left[2..12\right)$ $\hour$ before cooking.
\item Add broth and butter to a bowl, microwave just until melted.
\item Mix in remaining marinade ingredients and let cool.
\item Slowly inject the breast and thigh with $\approx 2~\teaspoon$ per site.\\
	Massage the meat; discard remaining marinade.
\item Cover turkey and refridgerate $2\plus$ $\hour$.
\item Prior to cooking, mix softened butter with the half the seasoning.
\item Slowly separate the skin from the breast muscle,\\
	work about half of the butter underneath the skin,\\
	rub the remaining around the outside.
\item Dust the remaining seasoning over the outside.
\item Tuck the wings into the sides with poultry lacers, untuck the legs.
\end{preparation}


\recipeend%
