\section[Double Duece]{Double Duece Chicken Rub\ragStars{3}}\label{double_duece_rub}


\begin{recipestats}[
	servings=1~\pound,
	preptime=10~\minute,
	original=Kevin \& Mike,
]
\end{recipestats}
\ragmarpar{Grill boneless chicken thighs for tacos, or BBQ chicken quarters.}


\begin{recipeabstract}
	A barbeque chicken collaboration.
	We prefer a 50 / 50 split between the two rubs for it's balanced flavor.
	The Pepper Rub works well on it's own for a traditional Barbeque, and the Chile Rub for tacos.
\end{recipeabstract}


\begin{ingredientcolumns}
	\begin{ingredientblock}[Single Duece Pepper Rub]
		\ingredient[1][\Tablespoon]{peppercorns}\\
		\ingredient[1][\Tablespoon]{mustard, yellow}\\
		\ingredient[1][\Tablespoon]{onion powder}\\
		\ingredient[1][\Tablespoon]{garlic powder}\\
		\ingredient[1][\Tablespoon]{celery seed}\\
		\ingredient[1][\Tablespoon]{Montreal Steak mix}
	\end{ingredientblock}
	\vfill\null
	\columnbreak

	\begin{ingredientblock}[Single Duece Chile Rub]
		\ingredient[1~\onehalf][\Tablespoon]{Guajillo powder}\\
		\ingredient[1][\Tablespoon]{salt, kosher}\\
		\ingredient[1][\Tablespoon]{paprika}\\
		\ingredient[\onehalf][\Tablespoon]{peppercorns}\\
		\ingredient[\onehalf][\Tablespoon]{nutmeg}\\
		\ingredient[\onehalf][\Tablespoon]{sage, ground}\\
		\ingredient[1][\teaspoon]{cayenne}\\
		\ingredient[1][\teaspoon]{brown sugar}
	\end{ingredientblock}
\end{ingredientcolumns}


\ragmarpar{You can eyeball each pepper rub ingredient instead of mixing it.}
\begin{preparation}
\item Prepare Pepper Rub.
	Coarsely grind pepper \& mustard seed, jar.
	Combine onion, garlic, celery, jar.
	Set aside Steak Seasoning.
\item Prepare Chile Rub.
	Grind the peppercorns, salt, sugar.
	Grind the nutmeg.
	Combine all, jar.
\item Prepare the chicken.
	Lightly coat first with garlic mix, then peppercorn mix, then Montreal Steak Seasoning.
\item Coat with Chile Rub using about as much as the Pepper Rub.
\item Marinate for $\approx$ $[\onehalf~..~6]$ \hour.
\end{preparation}


\recipeend%
